### 2015-05-04 paper.tex
Add article stub

\documentclass{article}

\begin{document}

\title{Title of paper}

\maketitle

Original paper by Axelrod and Hamilton \cite{1981-Axelrod-Hamilton}.

Some recent discussion of memory one strategies \cite{press2012iterated, stewart2012extortion}.

\bibliography{references.bib}
\bibliographystyle{unsrt}

\end{document}

### 2015-08-15 paper.tex
Putting initial structure of paper together
- Title
- Authors (alphabetical on first name - I don't care what we go for here)
- Sections
- Bullet points added for intro

@@
 \documentclass{article}
+
+% Nicer bibliography management
+\usepackage[backend=biber, backref=true, firstinits=true, url=true, isbn=true]{biblatex}
+\addbibresource{references.bib}
+%-----------------------------
+
+% Lazy page formating (we can adjust when submitting)
+\usepackage{fullpage}
+\usepackage[parfill]{parskip}
+%-----------------------------
+
+\title{An open reproducible framework for the study of the iterated prisoner's
+dilemma}
+
+\author{Karol Langner\\
+        \and
+        Marc Harper\\
+        \and
+        Owen Campbell\\
+        \and
+        Vincent Knight\\
+}
+
+\date{\today}
 
@@
 
-\title{Title of paper}
-
 \maketitle
 
-Original paper by Axelrod and Hamilton \cite{1981-Axelrod-Hamilton}.
+\section{Introduction}\label{sec:introduction}
 
-Some recent discussion of memory one strategies \cite{press2012iterated, stewart2012extortion}.
+\begin{itemize}
+\item Review of the tournament itself;
+      Original paper by Axelrod and Hamilton~\cite{1981-Axelrod-Hamilton}.
+      Some recent discussion of memory one strategies~\cite{press2012iterated, stewart2012extortion}.
 
-\bibliography{references.bib}
-\bibliographystyle{unsrt}
+\item Discussion about open reproducible science (there are some reference
+      around) (Python, git, github etc\dots)
+\item Overview of the library (what it can do, what has been done with it)
+\item Point at Sections~\ref{sec:reproducing-previous-tournaments}
+      and~\ref{sec:new-strategies-and-implications}.
+\end{itemize}
 
+\section{Reproducing previous tournaments}\label{sec:reproducing-previous-tournaments}
+
+\section{New strategies and implications}\label{sec:new-strategies-and-implications}
+
+\section{Conclusion}\label{sec:conclusion}
+
+\printbibliography
 \end{document}

### 2015-10-09 paper.tex
Renaming one of the sections.
Opening paragraphs of the introduction.

@@
 
-\author{Karol Langner\\
+\author{Owen Campbell\\
         \and
@@
         \and
-        Owen Campbell\\
+        Vincent Knight\\
         \and
-        Vincent Knight\\
+        Karol Langner\\
 }
@@
 \section{Introduction}\label{sec:introduction}
+
+In 1980, Axelrod wrote two papers:~\cite{Axelrod1980a,Axelrod1980b} which
+described a computer tournament that has been at the origin of a majority of
+game theoretic work~\cite{readallthepapers}.
+
+The tournament is based on an iterated game (see~\cite{Maschler2013} or similar
+for details) where two players repeatedly play the normal form game of
+(\ref{equ:one-shot}) in full knowledge of each others playing history to date:
+
+\begin{equation}
+    \begin{pmatrix}
+        3,3 & 0,5\\
+        5,0 & 1,1
+    \end{pmatrix}
+    \label{equ:one-shot}
+\end{equation}
+
+The game of (\ref{equ:one-shot}) is called the Prisoner's Dilemma. This is a game with the following rhetoric:
+
+\begin{quote}
+    Two players have committed some sort of crime and have been separated for
+    questioning, if they \textit{Cooperate} which each other and do not confess
+    they will receive a reduced sentence (corresponding to the advantageous utility
+    of \(3\) in (\ref{equ:one-shot})). If however, one of them cooperate and the
+    other \textit{Defects} then the cooperator will receive a heavier sentence
+    (corresponding to a utility of \(0\)) and the defector will be offered a deal
+    (corresponding to a utility of \(5\)). If both players defect they both receive
+    longer sentences (corresponding to a utility of \(1\)).
+\end{quote}
+
+Axelrod's tournaments (and further implementations of these) are sometimes
+referred to as Iterated Prisoner's Dilemma tournaments.
 
@@
 
-\section{New strategies and implications}\label{sec:new-strategies-and-implications}
+\section{New strategies, tournaments and implications}\label{sec:new-strategies-and-implications}
 

### 2015-10-11 paper.tex
Rewrite the start and desc of PD.

--- 2015-08-15 paper.tex
@@
 
+\usepackage{amsmath}
+\usepackage{hyperref}
+\usepackage{booktabs}
+
 \title{An open reproducible framework for the study of the iterated prisoner's
@@
 \section{Introduction}\label{sec:introduction}
+
+As stated in~\cite{Bendor2015}: ``\textit{few works in social science have had
+the general impact of [Axelrod's study of the evolution of cooperation]}''.  In
+1980, Axelrod wrote two papers:~\cite{Axelrod1980a,Axelrod1980b} which described
+a computer tournament that has been at the origin of a majority of game
+theoretic work~\cite{Banks1990, Bendor2015, Boyd1987, Chellapilla1999,
+    DavidB1993, Doebeli2005, Ellison1994, Gotts2003, Isaac2008, Kraines1989,
+    Lorberbaum1994, Milgrom1982, Molander1985, Murnighan2015, Press2012,
+Stephens2002, Stewart2012}. As described in~\cite{Bendor2015} this work has not
+only had mathematical impact but has also led to insights in biology (for
+example in~\cite{Chellapilla1999}, a real tournament where Blu Jays are the
+participants is described) and in particular to the study of evolution.
+
+The tournament is based on an iterated game (see~\cite{Maschler2013} or similar
+for details) where two players repeatedly play the normal form game of
+(\ref{equ:one-shot}) in full knowledge of each others playing history to date.
+An excellent description of the \textit{one shot} game is given
+in~\cite{Gotts2003} which is paraphrased below:
+
+Two players must choose between \textit{Cooperate} (\(C\)) and \textit{Defect}
+(\(D\)):
+
+\begin{itemize}
+    \item If both choose \(C\), they receive a payoff of \(R\)
+        (\textbf{R}eward);
+    \item If both choose \(D\), they receive a payoff of \(P\)
+        (\textbf{P}punishment);
+    \item If one chooses \(C\) and the other \(D\), the defector receives a
+        payoff of \(T\) (\textbf{T}emptation) and the cooperator a payoff of
+        \(S\) (\textbf{S}ucker).
+\end{itemize}
+
+\begin{equation}
+    \begin{pmatrix}
+        R,R & S,T\\
+        S,S & P,P
+    \end{pmatrix}\quad\text{such that } T>R>P>S \text{ and } 2R > T + S
+    \label{equ:one-shot}
+\end{equation}
+
+The game of (\ref{equ:one-shot}) is called the Prisoner's Dilemma. Numerical
+values of \((R,S,T,P)=(3,0,5,1)\) are often used in the literature. Axelrod's
+tournaments (and further implementations of these) are sometimes referred to as
+Iterated Prisoner's Dilemma tournaments.
 

### 2015-10-11 paper.tex
Fixing reference and adding skeleton table.

@@
 only had mathematical impact but has also led to insights in biology (for
-example in~\cite{Chellapilla1999}, a real tournament where Blu Jays are the
+example in~\cite{Stephens2002}, a real tournament where Blu Jays are the
 participants is described) and in particular to the study of evolution.
@@
 tournaments (and further implementations of these) are sometimes referred to as
-Iterated Prisoner's Dilemma tournaments.
+Iterated Prisoner's Dilemma tournaments, an overview of published tournaments is
+given in Table~\ref{tab:tournament}.
+
+\begin{table}[!hbtp]
+    \begin{center}
+        \begin{tabular}{ccccc}
+            \toprule
+            Year & Reference            & Number of Strategies & Type     & Reproducible\\
+            \midrule
+            1979 & \cite{Axelrod1980a}  & 13                   & Standard & With difficulty\\
+            1979 & \cite{Axelrod1980b}  & 64                   & Standard & With difficulty\\
+            \bottomrule
+        \end{tabular}
+    \end{center}
+    \caption{An overview of published tournaments}\label{tab:tournaments}
+\end{table}
 

### 2015-10-15 paper.tex
Adding some past tournament details to table.

--- 2015-10-11 paper.tex
@@
 
-As stated in~\cite{Bendor2015}: ``\textit{few works in social science have had
+As stated in~\cite{Bendor1991}: ``\textit{few works in social science have had
 the general impact of [Axelrod's study of the evolution of cooperation]}''.  In
-1980, Axelrod wrote two papers:~\cite{Axelrod1980a,Axelrod1980b} which described
-a computer tournament that has been at the origin of a majority of game
-theoretic work~\cite{Banks1990, Bendor2015, Boyd1987, Chellapilla1999,
-    DavidB1993, Doebeli2005, Ellison1994, Gotts2003, Isaac2008, Kraines1989,
-    Lorberbaum1994, Milgrom1982, Molander1985, Murnighan2015, Press2012,
-Stephens2002, Stewart2012}. As described in~\cite{Bendor2015} this work has not
-only had mathematical impact but has also led to insights in biology (for
-example in~\cite{Chellapilla1999}, a real tournament where Blu Jays are the
-participants is described) and in particular to the study of evolution.
+1980, Axelrod wrote two papers:~\cite{Axelrod1980a,Axelrod1980b} which
+described a computer tournament that has been at the origin of a majority of
+game theoretic work~\cite{Banks1990, Bendor1991, Boyd1987, Chellapilla1999,
+DavidB1993, Doebeli2005, Ellison1994, Gotts2003, Hilbe2013, Isaac2008,
+Kraines1989, Lee2015, Lorberbaum1994, Milgrom1982, Molander1985, Murnighan2015,
+Press2012, Stephens2002, Stewart2012}. As described in~\cite{Bendor1991} this
+work has not only had mathematical impact but has also led to insights in
+biology (for example in~\cite{Stephens2002}, a real tournament where Blu Jays
+are the participants is described) and in particular to the study of evolution.
 
@@
 tournaments (and further implementations of these) are sometimes referred to as
-Iterated Prisoner's Dilemma tournaments.
+Iterated Prisoner's Dilemma tournaments, an overview of published tournaments is
+given in Table~\ref{tab:tournaments}.
+
+\begin{table}[!hbtp]
+    \begin{center}
+        \begin{tabular}{ccccc}
+            \toprule
+            Year     & Reference           & Number of Strategies & Type     & Source Code\\
+            \midrule
+            1979     & \cite{Axelrod1980a} & 13                   & Standard & Not immediately available\\
+            1979     & \cite{Axelrod1980b} & 64                   & Standard & Not immediately available\\
+            1991     & \cite{Bendor1991}   & 13                   & Noisy    & Not immediately available\\
+            2002     & \cite{Stephens2002} & 16                   & Wildlife & Not applicable\\
+            % Is this worth including? If so I think we need more.
+            \bottomrule
+        \end{tabular}
+    \end{center}
+    \caption{An overview of published tournaments}\label{tab:tournaments}
+\end{table}
 

### 2015-10-16 paper.tex
First draft of review section and plan for description of lib.

@@
 \section{Introduction}\label{sec:introduction}
+
+This paper introduces a software package: the Axelrod python library
+\cite{Axelrod-Pythonprojectteam2015}. The Axelrod-Python project has the
+following stated goals:
+
+\begin{itemize}
+    \item To enable the reproduction of previous Iterated Prisoner's Dilemma
+    research as easily as possible.
+    \item To produce the de-facto tool for any future Iterated Prisoner's
+    Dilemma research.
+    \item To provide as simple a means as possible for anyone to define and
+    contribute new and original Iterated Prisoner's Dilemma strategies.
+\end{itemize}
+
+This library is motivated by an ongoing discussion in the academic community
+about reproducible research \cite{Crick2014a, Prlic2012, Sandve2013,
+Hong2015a}. The library is:
+
+\begin{itemize}
+    \item Open: all code is released under an MIT license;
+    \item Reproducible: at the time of writing there is an excellent level of
+        integrated tests with 99.59\% coverage;
+    \item Documented: all features of the library are documented for ease of
+        use.
+    \item Extensive: over 100 strategies are included.
+\end{itemize}
+
+Before describing the package in more detail in
+Section~\ref{sec:description-of-axelrod-python}, an overview of some previous
+Iterated Prisoner's Dilemma research will be given.
+
+\subsection{Review of the literature}\label{sec:review}
 
@@
 tournaments (and further implementations of these) are sometimes referred to as
-Iterated Prisoner's Dilemma tournaments, an overview of published tournaments is
+Iterated Prisoner's Dilemma (IPD) tournaments, an overview of published tournaments is
 given in Table~\ref{tab:tournaments}.
@@
 
+In \cite{Milgrom1982} describes how incomplete information can be used to
+enhance cooperation, in a similar approach to the proof of the Folk theorem for
+repeated games \cite{Maschler2013}. This aspect of incomplete information is
+also considered in \cite{Molander1985, Bendor1991, Lee2015} where ``noisy''
+tournaments randomly flip the choice made by a given strategy. In
+\cite{Murnighan2015} incomplete information is considered in the sense of a
+probabilistic termination of each round of the tournament.
+
+As mentioned before, IPD tournaments have been studied in an evolutionary
+context: \cite{Ellison1994, Lee2015, Press2012, Stewart2012} consider this in a
+traditional evolutionary game theory context. These works investigates
+particular evolutionary contexts within which cooperation can emerge as stable.
+Often these works consider direct opposition to another strategy and disregard
+the population dynamics, for example in \cite{Lee2015} a simple machine learning
+algorithm outperforms a strategy found in \cite{Press2012}.
+
+Further to these evolutionary ideas, \cite{Chellapilla1999, DavidB1993} are
+examples of using machine learning techniques to evolve particular strategies.
+In \cite{Axelrod} Axelrod describes how similar techniques are used to
+genetically evolve a high performing strategy from a given set of strategies.
+Note that in his original work Axelrod only used a base strategy set of 12
+strategies for this evolutionary study. This is noteworthy as
+\cite{Axelrod-Pythonprojectteam2015} now boasts over 90 strategies that are
+readily available for a similar analysis.
+
+\subsection{Description of the Axelrod python package}\label{sec:description-of-axelrod-python}.
+
 \begin{itemize}
-\item Review of the tournament itself;
-      Original paper by Axelrod and Hamilton~\cite{1981-Axelrod-Hamilton}.
-      Some recent discussion of memory one strategies~\cite{press2012iterated, stewart2012extortion}.
-
-\item Discussion about open reproducible science (there are some reference
-      around) (Python, git, github etc\dots)
-\item Overview of the library (what it can do, what has been done with it)
-\item Point at Sections~\ref{sec:reproducing-previous-tournaments}
-      and~\ref{sec:new-strategies-and-implications}.
+    \item Describe library,
+    \item Perhaps include image like:
+        http://vknight.org/Talks/2015-10-12-Evolutionary-mathematics/static/outline_of_library.svg
+        (am playing with https://pycallgraph.readthedocs.org/en/master/)
+    \item Show code to create basic tournament
+    \item Show code for a strategy
+    \item Show process to contribute strategy
 \end{itemize}

### 2015-10-16 tex/paper.tex
Reorganisation and first draft of intro.

--- 2015-10-16 paper.tex
@@
 
-\usepackage{amsmath}
-\usepackage{hyperref}
-\usepackage{booktabs}
+\usepackage{amsmath}  % Basic
+\usepackage{hyperref}  % Links etc
+\usepackage{booktabs}  % Better tables
+\usepackage{listings}  % Code
+\usepackage{graphicx}  % Images
 
@@
 
+The library is written in Python (\url{http://www.python.org/}) which is a
+popular language in the academic community with libraries developed for:
+
 \begin{itemize}
-    \item Describe library,
-    \item Perhaps include image like:
-        http://vknight.org/Talks/2015-10-12-Evolutionary-mathematics/static/outline_of_library.svg
-        (am playing with https://pycallgraph.readthedocs.org/en/master/)
-    \item Show code to create basic tournament
-    \item Show code for a strategy
-    \item Show process to contribute strategy
+    \item Machine learning (\url{http://scikit-learn.org/});
+    \item Visualisation (\url{http://matplotlib.org/});
+    \item Mathematics (\url{http://www.sagemath.org/}).
 \end{itemize}
+
+In \cite{Isaac2008} Python is described as an appropriate language for the
+reproduction of Iterated Prisoner's dilemma tournaments due to it's object
+oriented nature and readability.
+
+The library itself is available at
+\url{https://github.com/Axelrod-Python/Axelrod}. This is a hosted git repository
+which. Git is a popular version control system which is one of the recommended
+aspects of reproducible research \cite{Crick2014a, Sandve2013}.
+
+Figure~\ref{fig:demo_tournament_commands} shows a very simple example of using
+the library to create a basic tournament with the graphical output shown in
+Figure~\ref{fig:demo_tournament}.
+
+\begin{figure}[!hbtp]
+    \begin{lstlisting}[frame=single]
+>>> import axelrod
+>>> strategies = [s() for s in axelrod.demo_strategies])
+>>> tournament = axelrod.Tournament(strategies)
+>>> results = tournament.play()
+>>> plot = axelrod.Plot(results)
+>>> plot.boxplot()
+    \end{lstlisting}
+    \caption{A simple set of commands to create a demonstration tournament. The
+        output is shown in Figure~\ref{fig:demo_tournament}.}
+    \label{fig:demo_tournament_commands}
+\end{figure}
+
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[width=.8\textwidth]{../img/demo_tournament.pdf}
+    \caption{The results from a simple tournament.}
+    \label{fig:demo_tournament}
+\end{figure}
+
+This just shows the very basic utilisation of the library and further details
+can be found at the online documentation:
+\url{http://axelrod.readthedocs.org}. Some further implemented capabilities include:
+
+\begin{itemize}
+    \item Noisy tournaments;
+    \item Ecological tournaments;
+    \item Full tournament history.
+\end{itemize}
+
+As stated in Section~\ref{sec:introduction} one of the main goals of the library
+is to allow for the easy contribution of strategies. To do this requires the
+writing of a simple python class (which can inherit from other predefined
+classes). Full contribution guidelines can be found in the documentation.
+Figures~\ref{fig:grudger} and~\ref{fig:grudger_test} show the source code for
+the Grudger strategy as well as it's corresponding test.
+
+\begin{figure}[!hbtp]
+    \begin{lstlisting}[frame=single]
+class Grudger(Player):
+    """A player starts by cooperating however will defect if
+       at any point the opponent has defected."""
+
+    name = 'Grudger'
+    classifier = {
+        'memory_depth': float('inf'),  # Long memory
+        'stochastic': False,
+        'inspects_source': False,
+        'manipulates_source': False,
+        'manipulates_state': False
+    }
+
+    def strategy(self, opponent):
+        """Begins by playing C, then plays D for the remaining
+           rounds if the opponent ever plays D."""
+        if opponent.defections:
+            return D
+        return C
+    \end{lstlisting}
+    \caption{Source code for the Grudger strategy.}
+    \label{fig:grudger}
+\end{figure}
+
+\begin{figure}[!hbtp]
+    \begin{lstlisting}[frame=single]
+class TestGrudger(TestPlayer):
+
+    name = "Grudger"
+    player = axelrod.Grudger
+    expected_classifier = {
+        'memory_depth': float('inf'),  # Long memory
+        'stochastic': False,
+        'inspects_source': False,
+        'manipulates_source': False,
+        'manipulates_state': False
+    }
+
+    def test_initial_strategy(self):
+        """
+        Starts by cooperating
+        """
+        self.first_play_test(C)
+
+    def test_strategy(self):
+        """
+        If opponent defects at any point then the player will defect forever
+        """
+        self.responses_test([C, D, D, D], [C, C, C, C], [C])
+        self.responses_test([C, C, D, D, D], [C, D, C, C, C], [D])
+    \end{lstlisting}
+    \caption{Source code for the Grudger strategy.}
+    \label{fig:grudger}
+\end{figure}
+
+You can see an overview of some of the source code in Figure~\ref{fig:overview}.
+
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[width=.8\textwidth]{../img/outline_of_library.pdf}
+    \caption{An overview of the source code.}
+    \label{fig:overview}
+\end{figure}
+
+To date the library has had contributions from 19 contributors from a variety of
+backgrounds. These contributions have both been in terms of strategies (one
+strategy is the creation of an undergraduate mathematics student with little
+prior knowledge of programming) as well as the architecture of the library
+itself.
+
+Before discussing the novel insights obtained from the study of this library in
+Section~\ref{sec:new-strategies-and-implications} an overview of some
+tournaments that have been reproduced will be given in
+Section~\ref{sec:reproducing-previous-tournaments}.
 

### 2015-10-16 tex/paper.tex
Minor tidying.

@@
 This library is motivated by an ongoing discussion in the academic community
-about reproducible research \cite{Crick2014a, Prlic2012, Sandve2013,
-Hong2015a}. The library is:
+about reproducible research \cite{Crick2014a, Hong2015a, Prlic2012, Sandve2013},
+and is:
 
@@
 The library is written in Python (\url{http://www.python.org/}) which is a
-popular language in the academic community with libraries developed for:
+popular language in the academic community with libraries developed for a
+variety of uses including:
 
@@
     \item Visualisation (\url{http://matplotlib.org/});
-    \item Mathematics (\url{http://www.sagemath.org/}).
+    \item Mathematics (\url{http://www.sagemath.org/});
+    \item Astrophysics (\url{http://www.astropy.org/});
+    \item Data manipulation (\url{http://pandas.pydata.org/});
+    \item Algorithmic Game Theory (\url{http://gambit.sourceforge.net/)}).
 \end{itemize}
 
-In \cite{Isaac2008} Python is described as an appropriate language for the
+Furthermore \cite{Isaac2008} Python is described as an appropriate language for the
 reproduction of Iterated Prisoner's dilemma tournaments due to it's object
@@
 The library itself is available at
-\url{https://github.com/Axelrod-Python/Axelrod}. This is a hosted git repository
-which. Git is a popular version control system which is one of the recommended
-aspects of reproducible research \cite{Crick2014a, Sandve2013}.
+\url{https://github.com/Axelrod-Python/Axelrod}. This is a hosted git
+repository. Git is a popular version control system which is one of the
+recommended aspects of reproducible research \cite{Crick2014a, Sandve2013}.
+
+Installation of the library is straightforward as it is available via the
+standard Python installation package: `pip'
+(\url{https://pypi.python.org/pypi}). This ensures it can be used on all major
+operating systems (Windows, OS X and Linux).
 
 Figure~\ref{fig:demo_tournament_commands} shows a very simple example of using
-the library to create a basic tournament with the graphical output shown in
+the library to create a basic tournament giving the graphical output shown in
 Figure~\ref{fig:demo_tournament}.
@@
     \end{lstlisting}
-    \caption{Source code for the Grudger strategy.}
-    \label{fig:grudger}
+    \caption{Test code for the Grudger strategy.}
+    \label{fig:grudger_test}
 \end{figure}

### 2015-10-21 tex/paper.tex

@@
 work has not only had mathematical impact but has also led to insights in
-biology (for example in~\cite{Stephens2002}, a real tournament where Blu Jays
+biology (for example in~\cite{Stephens2002}, a real tournament where Blue Jays
 are the participants is described) and in particular to the study of evolution.
@@
 tournaments (and further implementations of these) are sometimes referred to as
-Iterated Prisoner's Dilemma (IPD) tournaments, an overview of published tournaments is
+Iterated Prisoner's Dilemma (IPD) tournaments. An overview of published tournaments is
 given in Table~\ref{tab:tournaments}.
@@
 
-In \cite{Milgrom1982} describes how incomplete information can be used to
+\cite{Milgrom1982} describes how incomplete information can be used to
 enhance cooperation, in a similar approach to the proof of the Folk theorem for
@@
 tournaments randomly flip the choice made by a given strategy. In
-\cite{Murnighan2015} incomplete information is considered in the sense of a
+\cite{Murnighan2015}, incomplete information is considered in the sense of a
 probabilistic termination of each round of the tournament.
@@
 context: \cite{Ellison1994, Lee2015, Press2012, Stewart2012} consider this in a
-traditional evolutionary game theory context. These works investigates
+traditional evolutionary game theory context. These works investigate
 particular evolutionary contexts within which cooperation can emerge as stable.
@@
 examples of using machine learning techniques to evolve particular strategies.
-In \cite{Axelrod} Axelrod describes how similar techniques are used to
+In \cite{Axelrod}, Axelrod describes how similar techniques are used to
 genetically evolve a high performing strategy from a given set of strategies.
-Note that in his original work Axelrod only used a base strategy set of 12
+Note that in his original work, Axelrod only used a base strategy set of 12
 strategies for this evolutionary study. This is noteworthy as
@@
 
-Furthermore \cite{Isaac2008} Python is described as an appropriate language for the
-reproduction of Iterated Prisoner's dilemma tournaments due to it's object
+Furthermore, \cite{Isaac2008} Python is described as an appropriate language for the
+reproduction of Iterated Prisoner's dilemma tournaments due to its object
 oriented nature and readability.
@@
 Figures~\ref{fig:grudger} and~\ref{fig:grudger_test} show the source code for
-the Grudger strategy as well as it's corresponding test.
+the Grudger strategy as well as its corresponding test.
 

### 2015-11-03 tex/paper.tex
References to more tournaments

@@
             1979     & \cite{Axelrod1980a} & 13                   & Standard & Not immediately available\\
-            1979     & \cite{Axelrod1980b} & 64                   & Standard & Not immediately available\\
+            1979     & \cite{Axelrod1980b} & 64                   & Standard & Available in FORTRAN\\
             1991     & \cite{Bendor1991}   & 13                   & Noisy    & Not immediately available\\
             2002     & \cite{Stephens2002} & 16                   & Wildlife & Not applicable\\
-            % Is this worth including? If so I think we need more.
+            2005     & \cite{kendall2007iterated} & 223           & Varied   & Not available \\
+            2012     & \cite{Stewart2012} & 13                    & Standard & Not fully available \\
             \bottomrule

### 2015-11-03 tex/paper.tex
Some material for the introduction, corrected citation.

@@
 
+Several iterated prisoner's dilemma tournaments have generated much interest,
+including Axelrod's original tournaments, two 2004 anniversary tournaments, and
+the S&P 2012 tournament following the discovery of zero-determinant strategies.
+Subsequent research has spawned an enormous number of papers, but rarely are the
+results reproducible. Among well-known tournaments, in only one case is the full
+original source code available (Axelrod's second tournament, in FORTRAN); in no
+cases is the available code well-documented, easily modifiable, or released
+with significant test suites.
+
+To make matters more complicated, often a newly-created strategy is studied in
+isolation by opponents chosen by the strategy's creators, and often such
+strategies are not sufficiently described to enable realiable recreation
+(in the absense of source code), with \cite{slany2007some} being a notable
+counter-example. In some cases strategies are revised without updates to their
+names or published implementations \cite{li2007design} \cite{li2011engineering}.
+As a result, some of the results related to these strategies and tournaments
+have not been reliably replicated, and have not met the basic scientific
+criterion of falsifiability.
+
 This paper introduces a software package: the Axelrod python library
@@
 \begin{itemize}
-    \item To enable the reproduction of previous Iterated Prisoner's Dilemma
-    research as easily as possible.
+    \item To enable the reproduction of Iterated Prisoner's Dilemma
+    research as easily as possible
     \item To produce the de-facto tool for any future Iterated Prisoner's
-    Dilemma research.
+    Dilemma research
     \item To provide as simple a means as possible for anyone to define and
-    contribute new and original Iterated Prisoner's Dilemma strategies.
+    contribute new and original Iterated Prisoner's Dilemma strategies
 \end{itemize}
@@
     \item Open: all code is released under an MIT license;
-    \item Reproducible: at the time of writing there is an excellent level of
-        integrated tests with 99.59\% coverage;
-    \item Documented: all features of the library are documented for ease of
-        use.
-    \item Extensive: over 100 strategies are included.
+    \item Reproducible and well-tested: at the time of writing there is an excellent level of
+        integrated tests with 99.59\% coverage
+    \item Well-documented: all features of the library are documented for ease of
+        use and modification
+    \item Extensive: over 100 strategies are included, with infinitely-many
+    strategies available in the case of parameterized strategies
+    \item Extensible: easy to modify to include new strategies and to run new tournaments
 \end{itemize}

### 2015-11-03 tex/paper.tex
Various additions/edits

@@
 isolation by opponents chosen by the strategy's creators, and often such
-strategies are not sufficiently described to enable realiable recreation
+strategies are not sufficiently described to enable reliable recreation
 (in the absense of source code), with \cite{slany2007some} being a notable
@@
 \begin{itemize}
-    \item Noisy tournaments;
-    \item Ecological tournaments;
-    \item Full tournament history.
+    \item Noisy tournaments
+    \item Ecological tournaments
+    \item Full tournament history
+    \item Creation of plots of distributions of scores and wins
 \end{itemize}
@@
 
+S&P 2012 is fully reproducible; results are unstable (e.g. substituting soft_majo for
+hard_majo changes the results). ZD strategies do not fare well in many tournaments.
+
 \section{New strategies, tournaments and implications}\label{sec:new-strategies-and-implications}

### 2015-11-04 tex/paper.tex
Ideas for implications section

@@
 S&P 2012 is fully reproducible; results are unstable (e.g. substituting soft_majo for
-hard_majo changes the results). ZD strategies do not fare well in many tournaments.
+hard_majo changes the results).
 
 \section{New strategies, tournaments and implications}\label{sec:new-strategies-and-implications}
+
+Ideas for this section:
+* ZD strategies -- extortionate strategies win well but no ZDs score partiocualrly well,
+even ZDGTFT2
+* TFT, T2FT, TF2T -- no so great but variants with e.g. deadlock breaking, such as OmegaTFT,
+fare well
+* It's posible to win many matchups as well score highly -- backstabber, doublecrosser,
+foolmeonce, gruder
+* It's possible to be generally cooperative and still exploit naive strategies effective,
+such as LookerUp and MetaHunter
+* Long memory strategies are generally better
+* Meta strategies fare very well in general
+* Variance of score distributions is surprisingly low
+
+Plot of memory_depth vs mean score, mean wins?
 

### 2015-11-25 tex/paper.tex

--- 2015-11-03 tex/paper.tex
@@
 S&P 2012 is fully reproducible; results are unstable (e.g. substituting soft_majo for
-hard_majo changes the results). ZD strategies do not fare well in many tournaments.
+hard_majo changes the results).
 
 \section{New strategies, tournaments and implications}\label{sec:new-strategies-and-implications}
+
+Ideas for this section:
+* ZD strategies -- extortionate strategies win well but no ZDs score partiocualrly well,
+even ZDGTFT2. With noise the ZD strategies don't win well either.
+* TFT, T2FT, TF2T -- no so great but variants with e.g. deadlock breaking, such as OmegaTFT,
+fare well
+* It's posible to win many matchups as well score highly -- backstabber, doublecrosser,
+foolmeonce. These strategies also score well in noisy tournaments
+* It's possible to be generally cooperative and still exploit naive strategies effective,
+such as LookerUp and MetaHunter
+* Long memory strategies are generally better
+* Meta strategies fare very well in general, also in noisy tournaments
+* Variance of score distributions is surprisingly low
+
+Plot of memory_depth vs mean score, mean wins?
 

### 2015-11-25 tex/paper.tex
Fixing some LaTeX.
I know it's still temporary but the document compiles now.

@@
 including Axelrod's original tournaments, two 2004 anniversary tournaments, and
-the S&P 2012 tournament following the discovery of zero-determinant strategies.
-Subsequent research has spawned an enormous number of papers, but rarely are the
-results reproducible. Among well-known tournaments, in only one case is the full
-original source code available (Axelrod's second tournament, in FORTRAN); in no
-cases is the available code well-documented, easily modifiable, or released
-with significant test suites.
+the Stewart and Plotkin 2012 tournament following the discovery of
+zero-determinant strategies.  Subsequent research has spawned an enormous number
+of papers, but rarely are the results reproducible. Among well-known
+tournaments, in only one case is the full original source code available
+(Axelrod's second tournament, in FORTRAN); in no cases is the available code
+well-documented, easily modifiable, or released with significant test suites.
 
@@
 counter-example. In some cases strategies are revised without updates to their
-names or published implementations \cite{li2007design} \cite{li2011engineering}.
+names or published implementations \cite{li2007design, li2011engineering}.
 As a result, some of the results related to these strategies and tournaments
@@
 
-S&P 2012 is fully reproducible; results are unstable (e.g. substituting soft_majo for
-hard_majo changes the results).
+Stewart and Plotkin 2012 is fully reproducible; results are unstable (e.g.\
+substituting \texttt{soft\_majo} for \texttt{hard\_majo} changes the results).
 
@@
 
-Plot of memory_depth vs mean score, mean wins?
+%Plot of memory_depth vs mean score, mean wins?
 

### 2015-11-25 tex/paper.tex
Moving from listings to minted for code listings.

@@
 \usepackage{booktabs}  % Better tables
-\usepackage{listings}  % Code
+\usepackage{minted}  % Code
 \usepackage{graphicx}  % Images
@@
 \begin{figure}[!hbtp]
-    \begin{lstlisting}[frame=single]
+    \begin{minted}[breaklines, linenos, frame=lines]{python}
 >>> import axelrod
@@
 >>> plot.boxplot()
-    \end{lstlisting}
+    \end{minted}
     \caption{A simple set of commands to create a demonstration tournament. The
@@
 \begin{figure}[!hbtp]
-    \begin{lstlisting}[frame=single]
+    \begin{minted}[breaklines, linenos, frame=lines]{python}
 class Grudger(Player):
@@
         return C
-    \end{lstlisting}
+    \end{minted}
     \caption{Source code for the Grudger strategy.}
@@
 \begin{figure}[!hbtp]
-    \begin{lstlisting}[frame=single]
+    \begin{minted}[breaklines, linenos, frame=lines]{python}
 class TestGrudger(TestPlayer):
@@
         self.responses_test([C, C, D, D, D], [C, D, C, C, C], [D])
-    \end{lstlisting}
+    \end{minted}
     \caption{Test code for the Grudger strategy.}

### 2015-12-05 scripts/number_of_strategies.py
Adding files to scrape git repo
Not sure this is quite working right.

@@ -1,0 +1,8 @@
+import axelrod
+from sys import argv
+
+try:
+    if type(len(axelrod.strategies)) is int:
+        print argv[1], len(axelrod.strategies), argv[2]
+except:
+    pass

### 2015-12-06 scripts/scrape_repo.py
Correcting the data.

@@ -1,0 +1,46 @@
+from git import Repo
+import axelrod
+import os
+import subprocess
+import time
+import csv
+
+
+path_to_repo = "../../../Axelrod"
+repo = Repo(path_to_repo)
+
+all_commits = [c for c in repo.iter_commits()]
+
+git = repo.git
+
+
+number_of_strategies = []
+dates = []
+git.checkout('master')
+
+try:
+    os.remove('data')
+except OSError:
+    pass
+
+for c in sorted(all_commits, key=lambda x:x.committed_date):
+
+    for rubbish in [".DS_Store",
+                    "axelrod/.DS_Store",
+                    "axelrod/tests/.DS_Store",
+                    "axelrod/strategies/.DS_Store"]:  # Having to delete some files that were not in gitignore at the time of the commit
+        try:
+            os.remove(path_to_repo + rubbish)
+        except OSError:
+            pass
+
+    git.checkout(c)
+
+    try:
+        subprocess.call(['python2', '-B', 'number_of_strategies.py', str(c.committed_date), c.hexsha])
+        dates.append(c.committed_date)
+
+    except ImportError:
+        pass
+
+git.checkout('master')

### 2015-12-06 scripts/number_of_strategies.py
Correcting the data.

@@ -1,8 +1,42 @@
-import axelrod
 from sys import argv
+import csv
+
 
 try:
-    if type(len(axelrod.strategies)) is int:
-        print argv[1], len(axelrod.strategies), argv[2]
+    import axelrod
+
+    strategies = []
+
+    try:
+        if type(axelrod.strategies) is list:
+            strategies += axelrod.strategies
+    except (AttributeError, TypeError):
+        pass
+
+    try:
+        if type(axelrod.ordinary_strategies) is list:
+            strategies += axelrod.ordinary_strategies
+    except (AttributeError, TypeError):
+        pass
+
+    try:
+        if type(axelrod.basic_strategies) is list:
+            strategies += axelrod.basic_strategies
+    except (AttributeError, TypeError):
+        pass
+
+    try:
+        if type(axelrod.cheating_strategies) is list:
+            strategies += axelrod.cheating_strategies
+    except (AttributeError, TypeError):
+        pass
+
+    count = len(set(strategies))
+
+    f = open('data', 'a')
+    csvwrtr = csv.writer(f)
+    csvwrtr.writerow([argv[1], count, argv[2]])
+    f.close()
+
 except:
     pass

### 2015-12-06 tex/paper.tex
Pointing at label.
Adding to section about reproducing tournaments.
Have code.
Could possibly be nice to include example/details about how far we are
from Axelrod's first tournament.

@@
 
-This just shows the very basic utilisation of the library and further details
-can be found at the online documentation:
-\url{http://axelrod.readthedocs.org}. Some further implemented capabilities include:
+Figure \ref{fig:demo_tournament_commands} just shows the very basic utilisation
+of the library and further details can be found at the online documentation:
+\url{http://axelrod.readthedocs.org}. Some further implemented capabilities
+include:
 
@@
 
-Stewart and Plotkin 2012 is fully reproducible; results are unstable (e.g.\
-substituting \texttt{soft\_majo} for \texttt{hard\_majo} changes the results).
+Due to the open nature of the library the number of strategies included has
+grown at a fast pace, as can be seen in
+Figure~\ref{fig:number_of_strategies_against_date}. Despite this, due to
+previous research being done in an irreproducible way due to, for example no
+source code, and/or vaguely described strategies; not all previous tournaments
+are yet to be reproduced.
+
+\begin{figure}[!hbtp] \centering
+    \includegraphics[width=.8\textwidth]{../img/number_of_strategies_with_arima_projection.pdf}
+    \caption{The number of strategies included in the library}
+    \label{fig:number_of_strategies_against_date}
+\end{figure}
+
+One tournament that is possible to reproduce is that of
+\cite{Stewart2012}. The strategies used in that tournament are the following:
+
+\begin{enumerate}
+    \item Cooperator
+    \item Defector
+    \item ZD-Extort-2
+    \item Joss: 0.9
+    \item Hard Tit For Tat
+    \item Hard Tit For 2 Tats
+    \item Tit For Tat
+    \item Grudger
+    \item Tit For 2 Tats
+    \item Win-Stay Lose-Shift
+    \item Random: 0.5
+    \item ZD-GTFT-2
+    \item GTFT: 0.33
+    \item Hard Prober
+    \item Prober
+    \item Prober 2
+    \item Prober 3
+    \item Calculator
+    \item Hard Go By Majority
+\end{enumerate}
+
+This can be reproduced as shown in Figure~\ref{fig:stewart-code}, which gives
+the plot of Figure~\ref{fig:stewart_tournament}.
+
+\begin{figure}[!hbtp]
+    \begin{minted}[breaklines, linenos, frame=lines]{python}
+>>> import axelrod
+
+>>> strategies = [axelrod.Cooperator(),
+....              axelrod.Defector(),
+....              axelrod.ZDExtort2(),
+....              axelrod.Joss(),
+....              axelrod.HardTitForTat(),
+....              axelrod.HardTitFor2Tats(),
+....              axelrod.TitForTat(),
+....              axelrod.Grudger(),
+....              axelrod.TitFor2Tats(),
+....              axelrod.WinStayLoseShift(),
+....              axelrod.Random(),
+....              axelrod.ZDGTFT2(),
+....              axelrod.GTFT(),
+....              axelrod.HardProber(),
+....              axelrod.Prober(),
+....              axelrod.Prober2(),
+....              axelrod.Prober3(),
+....              axelrod.Calculator(),
+....              axelrod.HardGoByMajority()]
+>>> tournament = axelrod.Tournament(strategies)
+>>> results = tournament.play()
+>>> plot = axelrod.Plot(results)
+>>> p = plot.boxplot()
+    \end{minted}
+    \caption{Source code for the Grudger strategy.}
+    \label{fig:stewart-code}
+\end{figure}
+
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[width=.8\textwidth]{../img/stewart_tournament.pdf}
+    \caption{The results from a simple tournament.}
+    \label{fig:stewart_tournament}
+\end{figure}
+
+Work is actively ongoing to include more strategies. In the next Section, an
+overview of some of the early and novel research insights made possible by the
+library.
 

### 2015-12-06 scripts/number_of_strategies.py
Adding some docstrings to scripts.

@@ -1,3 +1,11 @@
+"""
+A script to write the number of available strategies in the library to a data
+file. This is used in conjunction with scrape_repo.py to obtain the number of
+strategies at any given commit.
+
+A big thanks must go to Mario Wenzel for the discussion about this here:
+http://vknight.org/unpeudemath/code/2015/12/05/I-think-this-is-the-way-to-crawl-a-git-repository/
+"""
 from sys import argv
 import csv
 

### 2015-12-06 scripts/scrape_repo.py

@@ -1,3 +1,9 @@
+"""
+A script to walk through all commits of a repository.
+
+Works with `number_of_strategies.py` to get the number of strategies in the
+library at each commit.
+"""
 from git import Repo
 import axelrod
 import os

### 2015-12-06 tex/paper.tex
Adding doctests (because we can)
I don't think we want the skip in the final document but for now...

@@
 >>> import axelrod
->>> strategies = [s() for s in axelrod.demo_strategies])
+>>> strategies = [s() for s in axelrod.demo_strategies]
 >>> tournament = axelrod.Tournament(strategies)
@@
 >>> plot = axelrod.Plot(results)
->>> plot.boxplot()
+>>> plot.boxplot()  # doctest:+SKIP
     \end{minted}
@@
 >>> strategies = [axelrod.Cooperator(),
-....              axelrod.Defector(),
-....              axelrod.ZDExtort2(),
-....              axelrod.Joss(),
-....              axelrod.HardTitForTat(),
-....              axelrod.HardTitFor2Tats(),
-....              axelrod.TitForTat(),
-....              axelrod.Grudger(),
-....              axelrod.TitFor2Tats(),
-....              axelrod.WinStayLoseShift(),
-....              axelrod.Random(),
-....              axelrod.ZDGTFT2(),
-....              axelrod.GTFT(),
-....              axelrod.HardProber(),
-....              axelrod.Prober(),
-....              axelrod.Prober2(),
-....              axelrod.Prober3(),
-....              axelrod.Calculator(),
-....              axelrod.HardGoByMajority()]
+...               axelrod.Defector(),
+...               axelrod.ZDExtort2(),
+...               axelrod.Joss(),
+...               axelrod.HardTitForTat(),
+...               axelrod.HardTitFor2Tats(),
+...               axelrod.TitForTat(),
+...               axelrod.Grudger(),
+...               axelrod.TitFor2Tats(),
+...               axelrod.WinStayLoseShift(),
+...               axelrod.Random(),
+...               axelrod.ZDGTFT2(),
+...               axelrod.GTFT(),
+...               axelrod.HardProber(),
+...               axelrod.Prober(),
+...               axelrod.Prober2(),
+...               axelrod.Prober3(),
+...               axelrod.Calculator(),
+...               axelrod.HardGoByMajority()]
 >>> tournament = axelrod.Tournament(strategies)
@@
 >>> plot = axelrod.Plot(results)
->>> p = plot.boxplot()
+>>> plot.boxplot()  # doctest:+SKIP
     \end{minted}

### 2015-12-19 tex/paper.tex
full tournament and Lookerup

@@
     \includegraphics[width=.8\textwidth]{../img/stewart_tournament.pdf}
-    \caption{The results from a simple tournament.}
+    \caption{The results from \cite{Stewart2012}.}
     \label{fig:stewart_tournament}
@@
 \section{New strategies, tournaments and implications}\label{sec:new-strategies-and-implications}
+
+In parallel to the Python library, a tournament is being kept up to date that
+pits all strategies against each other. Figure \ref{fig:tournament} shows the
+results from the full tournament.
+
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[width=.8\textwidth]{../img/tournament.pdf}
+    \caption{Results from the library tournament (2015-12-19)}
+    \label{fig:tournament}
+\end{figure}
+
+The current winning strategy is a novel strategy of type: \textbf{LookerUp}. This
+is a strategy that maps a given set of states to actions. The state space is
+defined generically by \(m, n\) so as to map states to actions in the following
+way:
+
+\[(\underbrace{(C, D, D, D, C, D, D, C)}_{m\text{ first actions by opponent}},
+\overbrace{((C, C), (C, C))}^{n\text{ last pairs of actions}}) \to D\]
+
+The above example is an incomplete illustration of the mapping for \(m=8, n=2\).
+Intuitively this state space uses the initial plays of the opponent to gain some
+information about the intentions of it whilst still taking in to account the
+recent play.  The actual winning strategy an instance of the this framework for
+\(m=n=2\) for which an evolutionary algorithm has been used to train it. More
+details of this can be found in \cite{mojones}.
 

### 2016-01-30 tex/paper.tex
Making some details more verbose.
This could certainly be expanded.

@@
     \end{minted}
-    \caption{Source code for the Grudger strategy.}
+    \caption{Source code for reproducing the tournament of \cite{Stewart2012}}
     \label{fig:stewart-code}
@@
 In parallel to the Python library, a tournament is being kept up to date that
-pits all strategies against each other. Figure \ref{fig:tournament} shows the
+pits all strategies against each other. Figure~\ref{fig:tournament} shows the
 results from the full tournament.
@@
 \(m=n=2\) for which an evolutionary algorithm has been used to train it. More
-details of this can be found in \cite{mojones}.
+details of this can be found in \cite{mojones}. In \cite{} experiments are
+carried out to evaluate how this particular strategy behaves in environments
+other than those in which it was trained\dots
 
-Ideas for this section:
-* ZD strategies -- extortionate strategies win well but no ZDs score partiocualrly well,
-even ZDGTFT2. With noise the ZD strategies don't win well either.
-* TFT, T2FT, TF2T -- no so great but variants with e.g. deadlock breaking, such as OmegaTFT,
-fare well
-* It's posible to win many matchups as well score highly -- backstabber, doublecrosser,
-foolmeonce. These strategies also score well in noisy tournaments
-* It's possible to be generally cooperative and still exploit naive strategies effective,
-such as LookerUp and MetaHunter
-* Long memory strategies are generally better
-* Meta strategies fare very well in general, also in noisy tournaments
-* Variance of score distributions is surprisingly low
+There are various other insights that have been gained from ongoing open
+research on the library. These include:
+
+\begin{itemize}
+    \item A closer look at zero determinant strategies, showing that
+        extortionate strategies obtain a large number of wins \textit{but} do
+        not perform particularly well. This is relevant given the findings of
+        \cite{Stewart2012} in which zero determinant strategies are shown to be
+        able to perform better than a given other strategy. This finding extends
+        to noisy tournaments (which are also implemented in the library).
+    \item This negative relationship between wins and performance does not
+        generalise, there are some strategies that perform well, both in terms
+        of matches won and overall performance: Back stabber, Double crosser and
+        Fool Me Once. These strategies continue to perform well in noisy
+        tournaments.
+    \item Strategies like LookerUp and MetaHunter seem to be generally
+        cooperative yet still exploit naive strategies. The MetaHunter strategy
+        is a particular type of Meta strategy which uses a variety of other
+        strategy behaviours to choose a best action. These strategies perform
+        very well in general and continue to do so in noisy tournaments.
+\end{itemize}
+
+Details for the above can be found at \cite{}.
 

### 2016-02-03 tex/paper.tex
Adding a conclusion.

@@
 
+This paper has presented a game theoretic software package that aims to address
+reproducibility of research in to the iterated prisoner's dilemma. Through the
+very nature of the development of this library, all open research and
+development, it has not only acquired a large number of strategies (120) but
+also already discovered various insights that will lead to further publications.
+
+The capabilities of the library mentioned above are not at all comprehensive, a
+list of the current abilities include:
+
+\begin{itemize}
+    \item Noisy tournaments;
+    \item Ecological analysis of tournaments;
+    \item Morality metrics based on \cite{Singer-Clark2014};
+    \item Transformation of strategies (in effect giving an infinite number of
+        strategies);
+    \item Classification of strategies according to multiple dimensions.
+\end{itemize}
+
+These capabilities are constantly being updated. Some immediate further work
+includes allowing for tournaments of probabilistic length as well as further
+implementation of known strategies
+
+The ability to readily have available a large number of strategies makes this
+tool an excellent and obvious example of the benefits of open research which
+should positively impact the game theoretic community.
+
 \printbibliography

### 2016-02-08 tex/paper.tex
Addressing minor comments from O and M.

@@
 \begin{figure}[!hbtp]
-    \begin{minted}[breaklines, linenos, frame=lines]{python}
+    \begin{minted}[linenos, frame=lines]{python}
 >>> import axelrod
@@
 \begin{figure}[!hbtp]
-    \begin{minted}[breaklines, linenos, frame=lines]{python}
+    \begin{minted}[linenos, frame=lines]{python}
 class Grudger(Player):
@@
 \begin{figure}[!hbtp]
-    \begin{minted}[breaklines, linenos, frame=lines]{python}
+    \begin{minted}[linenos, frame=lines]{python}
 class TestGrudger(TestPlayer):
@@
 Figure~\ref{fig:number_of_strategies_against_date}. Despite this, due to
-previous research being done in an irreproducible way due to, for example no
-source code, and/or vaguely described strategies; not all previous tournaments
-are yet to be reproduced.
+previous research being done in an irreproducible, with for example no
+source code, and/or vaguely described strategies, not all previous tournaments
+are yet to be reproduced. In fact, some of the early tournaments might be
+impossible to reproduce as the source code is forever lost, this library aims to
+prevent this from happening again in the future.
 
@@
 
-Work is actively ongoing to include more strategies. In the next Section, an
+Work is ongoing to include more strategies. In the next Section, an
 overview of some of the early and novel research insights made possible by the
-library.
+library is described.
 
@@
 Intuitively this state space uses the initial plays of the opponent to gain some
-information about the intentions of it whilst still taking in to account the
-recent play.  The actual winning strategy an instance of the this framework for
+information about its intentions whilst still taking in to account the
+recent play. The actual winning strategy is an instance of the framework for
 \(m=n=2\) for which an evolutionary algorithm has been used to train it. More
@@
         \cite{Stewart2012} in which zero determinant strategies are shown to be
-        able to perform better than a given other strategy. This finding extends
+        able to perform better than any other strategy. This finding extends
         to noisy tournaments (which are also implemented in the library).
     \item This negative relationship between wins and performance does not
-        generalise, there are some strategies that perform well, both in terms
-        of matches won and overall performance: Back stabber, Double crosser and
-        Fool Me Once. These strategies continue to perform well in noisy
-        tournaments.
+        generalise. There are some strategies that perform well, both in terms
+        of matches won and overall performance: Back stabber, Double crosser,
+        Looker Up, and Fool Me Once. These strategies continue to perform well in noisy
+        tournaments, however some of these have knowledge of the length of the
+        game (Back stabber and Double crosser). This is not necessary to rank
+        well in both wins and score as demonstrated by Looker Up and Fool Me
+        Once.
     \item Strategies like LookerUp and MetaHunter seem to be generally
@@
 This paper has presented a game theoretic software package that aims to address
-reproducibility of research in to the iterated prisoner's dilemma. Through the
-very nature of the development of this library, all open research and
-development, it has not only acquired a large number of strategies (120) but
-also already discovered various insights that will lead to further publications.
+reproducibility of research into the iterated prisoner's dilemma. The open
+nature of the development of the library has lead rapidly to the inclusion of
+many well known strategies, many novel strategies, and new and recapitulated
+insights.
 

### 2016-02-08 tex/paper.tex
Changing penultimate sections.
Merging the later two sections and various other clean ups.

@@
 including Axelrod's original tournaments, two 2004 anniversary tournaments, and
-the Stewart and Plotkin 2012 tournament following the discovery of
-zero-determinant strategies.  Subsequent research has spawned an enormous number
-of papers, but rarely are the results reproducible. Among well-known
-tournaments, in only one case is the full original source code available
-(Axelrod's second tournament, in FORTRAN); in no cases is the available code
-well-documented, easily modifiable, or released with significant test suites.
+the Stewart and Plotkin 2012 tournament \cite{Stewart2012} following the
+discovery of zero-determinant strategies.  Subsequent research has spawned an
+enormous number of papers, but rarely are the results reproducible. Among
+well-known tournaments, in only one case is the full original source code
+available (Axelrod's second tournament, in FORTRAN); in no cases is the
+available code well-documented, easily modifiable, or released with significant
+test suites.
 
@@
 
-This paper introduces a software package: the Axelrod python library
+This paper introduces a software package: the Axelrod Python library
 \cite{Axelrod-Pythonprojectteam2015}. The Axelrod-Python project has the
@@
 Section~\ref{sec:description-of-axelrod-python}, an overview of some previous
-Iterated Prisoner's Dilemma research will be given.
+Iterated Prisoner's Dilemma research will be given in
+Section~\ref{sec:review}.
 
@@
 tournaments (and further implementations of these) are sometimes referred to as
-Iterated Prisoner's Dilemma (IPD) tournaments. An overview of published tournaments is
-given in Table~\ref{tab:tournaments}.
+Iterated Prisoner's Dilemma (IPD) tournaments. An incomplete overview of
+published tournaments is given in Table~\ref{tab:tournaments}.
 
@@
 
-\cite{Milgrom1982} describes how incomplete information can be used to
-enhance cooperation, in a similar approach to the proof of the Folk theorem for
-repeated games \cite{Maschler2013}. This aspect of incomplete information is
-also considered in \cite{Molander1985, Bendor1991, Lee2015} where ``noisy''
-tournaments randomly flip the choice made by a given strategy. In
+In \cite{Milgrom1982} a description is given of how incomplete information can
+be used to enhance cooperation, in a similar approach to the proof of the Folk
+theorem for repeated games \cite{Maschler2013}. This aspect of incomplete
+information is also considered in \cite{Molander1985, Bendor1991, Lee2015} where
+``noisy'' tournaments randomly flip the choice made by a given strategy. In
 \cite{Murnighan2015}, incomplete information is considered in the sense of a
@@
 Often these works consider direct opposition to another strategy and disregard
-the population dynamics, for example in \cite{Lee2015} a simple machine learning
+the population dynamics, for example in \cite{Lee2015} a machine learning
 algorithm outperforms a strategy found in \cite{Press2012}.
@@
 strategies for this evolutionary study. This is noteworthy as
-\cite{Axelrod-Pythonprojectteam2015} now boasts over 90 strategies that are
+\cite{Axelrod-Pythonprojectteam2015} now boasts over 120 strategies that are
 readily available for a similar analysis.
 
-\subsection{Description of the Axelrod python package}\label{sec:description-of-axelrod-python}.
+\subsection{Description of the Axelrod Python package}\label{sec:description-of-axelrod-python}
 
@@
 
-Figure \ref{fig:demo_tournament_commands} just shows the very basic utilisation
+Figure~\ref{fig:demo_tournament_commands} just shows the very basic utilisation
 of the library and further details can be found at the online documentation:
-\url{http://axelrod.readthedocs.org}. Some further implemented capabilities
-include:
-
-\begin{itemize}
-    \item Noisy tournaments
-    \item Ecological tournaments
-    \item Full tournament history
-    \item Creation of plots of distributions of scores and wins
-\end{itemize}
+\url{http://axelrod.readthedocs.org}.
 
@@
 is to allow for the easy contribution of strategies. To do this requires the
-writing of a simple python class (which can inherit from other predefined
+writing of a simple Python class (which can inherit from other predefined
 classes). Full contribution guidelines can be found in the documentation.
-Figures~\ref{fig:grudger} and~\ref{fig:grudger_test} show the source code for
+As an example, Figures~\ref{fig:grudger} and~\ref{fig:grudger_test} show the source code for
 the Grudger strategy as well as its corresponding test.
+You can see an overview of the structure of the source code in Figure~\ref{fig:overview}.
 
@@
 
-You can see an overview of some of the source code in Figure~\ref{fig:overview}.
-
 \begin{figure}[!hbtp]
@@
 
-To date the library has had contributions from 19 contributors from a variety of
+To date the library has had contributions from 24 contributors from a variety of
 backgrounds. These contributions have both been in terms of strategies (one
@@
 
-Before discussing the novel insights obtained from the study of this library in
-Section~\ref{sec:new-strategies-and-implications} an overview of some
-tournaments that have been reproduced will be given in
-Section~\ref{sec:reproducing-previous-tournaments}.
+Section~\ref{sec:new-strategies-and-implications} will describe in more detail
+some of research capabilities of the library.
 
-\section{Reproducing previous tournaments}\label{sec:reproducing-previous-tournaments}
+\section{New strategies, tournaments and implications}\label{sec:new-strategies-and-implications}
 
@@
 
-Work is ongoing to include more strategies. In the next Section, an
-overview of some of the early and novel research insights made possible by the
-library is described.
-
-\section{New strategies, tournaments and implications}\label{sec:new-strategies-and-implications}
-
 In parallel to the Python library, a tournament is being kept up to date that
-pits all strategies against each other. Figure~\ref{fig:tournament} shows the
-results from the full tournament.
+pits all available strategies against each other. Figure~\ref{fig:tournament}
+shows the results from the full tournament which can also be seen (in full
+detail) here: \url{http://axelrod-tournament.readthedocs.org/}.
 
@@
 
-The current winning strategy is a novel strategy of type: \textbf{LookerUp}. This
+The current winning strategy is a novel strategy called: Looker Up. This
 is a strategy that maps a given set of states to actions. The state space is
@@
 The above example is an incomplete illustration of the mapping for \(m=8, n=2\).
-Intuitively this state space uses the initial plays of the opponent to gain some
-information about its intentions whilst still taking in to account the
+Intuitively, this state space uses the initial plays of the opponent to gain
+some information about its intentions whilst still taking in to account the
 recent play. The actual winning strategy is an instance of the framework for
 \(m=n=2\) for which an evolutionary algorithm has been used to train it. More
-details of this can be found in \cite{mojones}. In \cite{} experiments are
-carried out to evaluate how this particular strategy behaves in environments
-other than those in which it was trained\dots
+details of this can be found at
+\url{http://mojones.net/evolving-strategies-for-an-iterated-prisoners-dilemma-tournament.html}.
+At
+\url{http://vknight.org/unpeudemath/gametheory/2015/11/28/Experimenting-with-a-high-performing-evolved-strategy-in-other-environments/}
+experiments are described that evaluate how this particular strategy behaves in
+environments other than those in which it was trained\dots
 
@@
 
-Details for the above can be found at \cite{}.
-
-%Plot of memory_depth vs mean score, mean wins?
+Details for the above can be found at \url{http://marcharper.codes/}.
 

### 2016-02-08 tex/paper.tex
Correct references + tidying images
- Adding references for the web links
- Grouping some images together

@@
 \usepackage{graphicx}  % Images
+\usepackage{subcaption}  % Subfigures
 
@@
 \begin{figure}[!hbtp]
+	\begin{subfigure}{.5\textwidth}
 		\centering
-    \includegraphics[width=.8\textwidth]{../img/demo_tournament.pdf}
+		\includegraphics[width=\textwidth]{../img/demo_tournament.pdf}
 		\caption{The results from a simple tournament.}
 		\label{fig:demo_tournament}
+	\end{subfigure}
+	\begin{subfigure}{.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{../img/stewart_tournament.pdf}
+		\caption{The results from \cite{Stewart2012}.}
+		\label{fig:stewart_tournament}
+	\end{subfigure}
+	\caption{Summary plots produced by the library.}
 \end{figure}
@@
 the Grudger strategy as well as its corresponding test.
-You can see an overview of the structure of the source code in Figure~\ref{fig:overview}.
 
@@
 
+To date the library has had contributions from 24 contributors from a variety
+of backgrounds. These contributions have both been in terms of strategies (one
+strategy is the creation of an undergraduate mathematics student with little
+prior knowledge of programming) as well as the architecture of the library
+itself. You can see an overview of the structure of the source code in
+Figure~\ref{fig:overview}.
+
 \begin{figure}[!hbtp]
+	\begin{subfigure}{.5\textwidth}
 		\centering
-    \includegraphics[width=.8\textwidth]{../img/outline_of_library.pdf}
+		\includegraphics[width=\textwidth]{../img/outline_of_library.pdf}
 		\caption{An overview of the source code.}
 		\label{fig:overview}
+	\end{subfigure}
+	\begin{subfigure}{.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{../img/number_of_strategies_with_arima_projection.pdf}
+		\caption{The number of strategies included in the library}
+		\label{fig:number_of_strategies_against_date}
+	\end{subfigure}
+	\caption{An overview of the library.}
 \end{figure}
-
-To date the library has had contributions from 24 contributors from a variety of
-backgrounds. These contributions have both been in terms of strategies (one
-strategy is the creation of an undergraduate mathematics student with little
-prior knowledge of programming) as well as the architecture of the library
-itself.
 
@@
 prevent this from happening again in the future.
-
-\begin{figure}[!hbtp] \centering
-    \includegraphics[width=.8\textwidth]{../img/number_of_strategies_with_arima_projection.pdf}
-    \caption{The number of strategies included in the library}
-    \label{fig:number_of_strategies_against_date}
-\end{figure}
 
@@
 
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=.8\textwidth]{../img/stewart_tournament.pdf}
-    \caption{The results from \cite{Stewart2012}.}
-    \label{fig:stewart_tournament}
-\end{figure}
-
 In parallel to the Python library, a tournament is being kept up to date that
@@
 	\centering
-    \includegraphics[width=.8\textwidth]{../img/tournament.pdf}
+	\includegraphics[width=.9\textwidth]{../img/tournament.pdf}
 	\caption{Results from the library tournament (2015-12-19)}
@@
 
-The current winning strategy is a novel strategy called: Looker Up. This
-is a strategy that maps a given set of states to actions. The state space is
-defined generically by \(m, n\) so as to map states to actions in the following
-way:
+The current winning strategy is a novel strategy called: Looker Up. This is a
+strategy that maps a given set of states to actions. The state space is defined
+generically by \(m, n\) so as to map states to actions as shown
+in~(\ref{equ:example_of_lookerup}).
 
-\[(\underbrace{(C, D, D, D, C, D, D, C)}_{m\text{ first actions by opponent}},
-\overbrace{((C, C), (C, C))}^{n\text{ last pairs of actions}}) \to D\]
+\begin{equation}
+	(\underbrace{(C, D, D, D, C, D, D, C)}_{m\text{ first actions by opponent}},
+	\overbrace{((C, C), (C, C))}^{n\text{ last pairs of actions}}) \to D
+	\label{equ:example_of_lookerup}
+\end{equation}
 
-The above example is an incomplete illustration of the mapping for \(m=8, n=2\).
-Intuitively, this state space uses the initial plays of the opponent to gain
-some information about its intentions whilst still taking in to account the
-recent play. The actual winning strategy is an instance of the framework for
-\(m=n=2\) for which an evolutionary algorithm has been used to train it. More
-details of this can be found at
-\url{http://mojones.net/evolving-strategies-for-an-iterated-prisoners-dilemma-tournament.html}.
-At
-\url{http://vknight.org/unpeudemath/gametheory/2015/11/28/Experimenting-with-a-high-performing-evolved-strategy-in-other-environments/}
+The above example is an incomplete illustration of the mapping for \(m=8,
+n=2\). Intuitively, this state space uses the initial plays of the opponent to
+gain some information about its intentions whilst still taking in to account
+the recent play. The actual winning strategy is an instance of the framework
+for \(m=n=2\) for which an evolutionary algorithm has been used to train it.
+More details of this can be found in \cite{Jones2015}. In \cite{Knight2015}
 experiments are described that evaluate how this particular strategy behaves in
-environments other than those in which it was trained\dots
+environments other than those in which it was trained and it continues to
+perform strongly.
 
@@
 
-Details for the above can be found at \url{http://marcharper.codes/}.
+Details for the above can be found in \cite{Harper2015}.
 

### 2016-02-08 tex/paper.tex
Adding an abstract.

@@
 \maketitle
+
+\begin{abstract}
+    The Axelrod Python library is an open source package that allows for
+    reproducible game theoretic research in to the iterated Prisoner's Dilemma.
+    This area of research began in the 1980 but suffers from a lack of
+    documented and tested code. This library aims to address this.
+
+    With a growing collection of 120 strategies the library is also a platform
+    for an original tournament that in itself is of interest to the game
+    theoretic community.
+\end{abstract}
 

### 2016-02-08 tex/paper.tex
Updating the tournament also tweaking abs parskip.

--- 2016-02-08 tex/paper.tex
@@
 \maketitle
+
+\begin{abstract}
+\noindent
+    The Axelrod Python library is an open source package that allows for
+    reproducible game theoretic research in to the iterated Prisoner's Dilemma.
+    This area of research began in the 1980 but suffers from a lack of
+    documented and tested code. This library aims to address this.\\
+
+\noindent
+    With a growing collection of 120 strategies the library is also a platform
+    for an original tournament that in itself is of interest to the game
+    theoretic community.
+\end{abstract}
 

### 2016-02-09 tex/paper.tex
Various minor tweaks after a read through.

@@
     This area of research began in the 1980 but suffers from a lack of
-    documented and tested code. This library aims to address this.\\
+    documented and tested code.
 
@@
     theoretic community.
+
+\noindent
+    This paper describes the iterated Prisoner's Dilemma, the library and
+    insights gained from some novel research.
 \end{abstract}
@@
 well-known tournaments, in only one case is the full original source code
-available (Axelrod's second tournament, in FORTRAN); in no cases is the
-available code well-documented, easily modifiable, or released with significant
-test suites.
+available (Axelrod's second tournament \cite{Axelrod1980b}, in FORTRAN); in no
+cases is the available code well-documented, easily modifiable, or released with
+significant test suites.
 
@@
     \item Reproducible and well-tested: at the time of writing there is an excellent level of
-        integrated tests with 99.59\% coverage
+        integrated tests with 99.37\% coverage
     \item Well-documented: all features of the library are documented for ease of
         use and modification
-    \item Extensive: over 100 strategies are included, with infinitely-many
+    \item Extensive: 120 strategies are included, with infinitely-many
     strategies available in the case of parameterized strategies
@@
 Iterated Prisoner's Dilemma research will be given in
-Section~\ref{sec:review}.
+Section~\ref{sec:review}. Section~\ref{sec:new-strategies-and-implications} will
+describe some early research and a conclusion is offered in
+Section~\ref{sec:conclusion}.
 
@@
     \item If both choose \(D\), they receive a payoff of \(P\)
-        (\textbf{P}punishment);
+        (\textbf{P}unishment);
     \item If one chooses \(C\) and the other \(D\), the defector receives a
@@
 
-The game of (\ref{equ:one-shot}) is called the Prisoner's Dilemma. Numerical
-values of \((R,S,T,P)=(3,0,5,1)\) are often used in the literature. Axelrod's
-tournaments (and further implementations of these) are sometimes referred to as
-Iterated Prisoner's Dilemma (IPD) tournaments. An incomplete overview of
-published tournaments is given in Table~\ref{tab:tournaments}.
+The game of (\ref{equ:one-shot}) is called the Prisoner's Dilemma. Specific
+numerical values of \((R,S,T,P)=(3,0,5,1)\) are often used in the literature.
+Axelrod's tournaments (and further implementations of these) are sometimes
+referred to as Iterated Prisoner's Dilemma (IPD) tournaments. An incomplete
+overview of published tournaments is given in Table~\ref{tab:tournaments}.
 
@@
 
-Furthermore, \cite{Isaac2008} Python is described as an appropriate language for the
+Furthermore, in \cite{Isaac2008} Python is described as an appropriate language for the
 reproduction of Iterated Prisoner's dilemma tournaments due to its object
@@
 \url{https://github.com/Axelrod-Python/Axelrod}. This is a hosted git
-repository. Git is a popular version control system which is one of the
+repository. Git is a version control system which is one of the
 recommended aspects of reproducible research \cite{Crick2014a, Sandve2013}.
@@
 
-Figure~\ref{fig:demo_tournament_commands} just shows the very basic utilisation
+Figure~\ref{fig:demo_tournament_commands} shows the very basic utilisation
 of the library and further details can be found at the online documentation:
@@
 As stated in Section~\ref{sec:introduction} one of the main goals of the library
-is to allow for the easy contribution of strategies. To do this requires the
+is to allow for the easy contribution of strategies. Doing this requires the
 writing of a simple Python class (which can inherit from other predefined
@@
 	\includegraphics[width=.9\textwidth]{../img/tournament.pdf}
-	\caption{Results from the library tournament (2015-12-19)}
+	\caption{Results from the library tournament (2016-02-10)}
 	\label{fig:tournament}
@@
 
-The above example is an incomplete illustration of the mapping for \(m=8,
-n=2\). Intuitively, this state space uses the initial plays of the opponent to
-gain some information about its intentions whilst still taking in to account
-the recent play. The actual winning strategy is an instance of the framework
-for \(m=n=2\) for which an evolutionary algorithm has been used to train it.
-More details of this can be found in \cite{Jones2015}. In \cite{Knight2015}
-experiments are described that evaluate how this particular strategy behaves in
-environments other than those in which it was trained and it continues to
-perform strongly.
+The example of (\ref{equ:example_of_lookerup}) is an incomplete illustration of
+the mapping for \(m=8, n=2\). Intuitively, this state space uses the initial
+plays of the opponent to gain some information about its intentions whilst still
+taking in to account the recent play. The actual winning strategy is an instance
+of the framework for \(m=n=2\) for which an evolutionary algorithm has been used
+to train it.  More details of this can be found in \cite{Jones2015}. In
+\cite{Knight2015} experiments are described that evaluate how this particular
+strategy behaves in environments other than those in which it was trained and it
+continues to perform strongly.
 
@@
         Once.
-    \item Strategies like LookerUp and MetaHunter seem to be generally
+    \item Strategies like Looker Up and Meta Hunter seem to be generally
         cooperative yet still exploit naive strategies. The MetaHunter strategy

### 2016-02-25 tex/paper.tex
Changing a paragraph and adding missing word
See
https://github.com/Axelrod-Python/An-open-reproducible-framework-for-the-study-of-the-iterated-prisoners-dilemma/issues/16

@@
 traditional evolutionary game theory context. These works investigate
-particular evolutionary contexts within which cooperation can emerge as stable.
-Often these works consider direct opposition to another strategy and disregard
-the population dynamics, for example in \cite{Lee2015} a machine learning
-algorithm outperforms a strategy found in \cite{Press2012}.
+particular evolutionary contexts within which cooperation can evolve and
+persist. This can be in the context of direct interactions between strategies
+or population dynamics for populations of many players using a variety of
+strategies, which can lead to very different results. For example, in
+\cite{Lee2015} a machine learning algorithm in a population context outperforms
+strategies described in \cite{Press2012} and \cite{Stewart2012} that are
+claimed to dominate any evolutionary opponent in head-to-head interactions.
 
@@
 Figure~\ref{fig:number_of_strategies_against_date}. Despite this, due to
-previous research being done in an irreproducible, with for example no
+previous research being done in an irreproducible manner, with for example no
 source code, and/or vaguely described strategies, not all previous tournaments
 are yet to be reproduced. In fact, some of the early tournaments might be
-impossible to reproduce as the source code is forever lost, this library aims to
-prevent this from happening again in the future.
+impossible to reproduce as the source code is forever lost, this library aims
+to prevent this from happening again in the future.
 

### 2016-03-08 tex/paper.tex
Some tidbits in intro

@@
 \noindent
-    The Axelrod Python library is an open source package that allows for
-    reproducible game theoretic research in to the iterated Prisoner's Dilemma.
-    This area of research began in the 1980 but suffers from a lack of
-    documented and tested code.
+    The Axelrod library is an open source Python package that allows for
+    reproducible game theoretic research into the iterated Prisoner's Dilemma.
+    This area of research began in the 1980s but suffers from a lack of
+    documented and test code. The goal of the library is to provide such
+    a resource, with facilities the design new strategies and interactions
+    between them, as well as conducting tournaments and ecological simulations
+    for population of strategies.
 
 \noindent
-    With a growing collection of 120 strategies the library is also a platform
+    With a growing collection of 120 strategies the library is a also a platform
     for an original tournament that in itself is of interest to the game
@@
 \noindent
-    This paper describes the iterated Prisoner's Dilemma, the library and
-    insights gained from some novel research.
+    This paper describes the iterated Prisoner's Dilemma, the Axelrod library
+    and its development, and insights gained from some novel research.
 \end{abstract}
@@
 Several iterated prisoner's dilemma tournaments have generated much interest,
-including Axelrod's original tournaments, two 2004 anniversary tournaments, and
+including Axelrod's original tournaments \cite{Axelrod1980a,Axelrod1980b},
+two 2004 anniversary tournaments (ref?), and
 the Stewart and Plotkin 2012 tournament \cite{Stewart2012} following the
@@
 As a result, some of the results related to these strategies and tournaments
-have not been reliably replicated, and have not met the basic scientific
+cannot be reliably replicated, and therefore have not met the basic scientific
 criterion of falsifiability.
@@
 
-This library is motivated by an ongoing discussion in the academic community
+The presented library is partly motivated by an ongoing discussion in the academic community
 about reproducible research \cite{Crick2014a, Hong2015a, Prlic2012, Sandve2013},
@@
 1980, Axelrod wrote two papers:~\cite{Axelrod1980a,Axelrod1980b} which
-described a computer tournament that has been at the origin of a majority of
-game theoretic work~\cite{Banks1990, Bendor1991, Boyd1987, Chellapilla1999,
+describe a computer tournament that has been a imajor influence on
+subsequent game theoretic work~\cite{Banks1990, Bendor1991, Boyd1987, Chellapilla1999,
 DavidB1993, Doebeli2005, Ellison1994, Gotts2003, Hilbe2013, Isaac2008,
@@
 Press2012, Stephens2002, Stewart2012}. As described in~\cite{Bendor1991} this
-work has not only had mathematical impact but has also led to insights in
+work has not only had impact in mathematics but has also led to insights in
 biology (for example in~\cite{Stephens2002}, a real tournament where Blue Jays
-are the participants is described) and in particular to the study of evolution.
+are the participants is described) and in particular in the study of evolution.
 
@@
 
+and the following reward matrix results from the Cartesian product of
+two decision vectors $\langle C, D \rangle$,
+
 \begin{equation}
@@
 The game of (\ref{equ:one-shot}) is called the Prisoner's Dilemma. Specific
-numerical values of \((R,S,T,P)=(3,0,5,1)\) are often used in the literature.
+numerical values of \((R,S,T,P)=(3,0,5,1)\) are often used in the literature,
+although any satisfying the conditions in \ref{equ:one-shot} will yield similar results.
 Axelrod's tournaments (and further implementations of these) are sometimes
@@
     \end{center}
-    \caption{An overview of published tournaments}\label{tab:tournaments}
+    \caption{An overview of published tournaments (specify what "type" means)}\label{tab:tournaments}
 \end{table}
@@
 are yet to be reproduced. In fact, some of the early tournaments might be
-impossible to reproduce as the source code is forever lost, this library aims
+impossible to reproduce as the source code is forever lost, and this library aims
 to prevent this from happening again in the future.

### 2016-03-09 tex/paper.tex
Minor changes
- Fix grammatical error in sentence.
- Quick indication as to what tournament type means.
- Adding the fact that we can have the full tournament interactions.

@@
 numerical values of \((R,S,T,P)=(3,0,5,1)\) are often used in the literature,
-although any satisfying the conditions in \ref{equ:one-shot} will yield similar results.
-Axelrod's tournaments (and further implementations of these) are sometimes
-referred to as Iterated Prisoner's Dilemma (IPD) tournaments. An incomplete
-overview of published tournaments is given in Table~\ref{tab:tournaments}.
+although any satisfying the conditions in \ref{equ:one-shot} will yield similar
+results.  Axelrod's tournaments (and further implementations of these) are
+sometimes referred to as Iterated Prisoner's Dilemma (IPD) tournaments. An
+incomplete overview of published tournaments is given in
+Table~\ref{tab:tournaments}.
 
@@
     \end{center}
-    \caption{An overview of published tournaments (specify what "type" means)}\label{tab:tournaments}
+    \caption{An overview of a selection of published tournaments. Not all
+             tournaments were `standard' round robins; for more details
+             see the indicated references.}\label{tab:tournaments}
 \end{table}
@@
 are yet to be reproduced. In fact, some of the early tournaments might be
-impossible to reproduce as the source code is forever lost, and this library aims
+impossible to reproduce as the source code is forever lost. This library aims
 to prevent this from happening again in the future.
@@
     \item Classification of strategies according to multiple dimensions.
+    \item Gathering of full interaction history for all interactions.
 \end{itemize}
@@
 includes allowing for tournaments of probabilistic length as well as further
-implementation of known strategies
+implementation of known strategies.
 

### 2016-03-09 tex/paper.tex
Adding references for other python packages.

@@
 \begin{itemize}
-    \item Machine learning (\url{http://scikit-learn.org/});
-    \item Visualisation (\url{http://matplotlib.org/});
-    \item Mathematics (\url{http://www.sagemath.org/});
-    \item Astrophysics (\url{http://www.astropy.org/});
-    \item Data manipulation (\url{http://pandas.pydata.org/});
-    \item Algorithmic Game Theory (\url{http://gambit.sourceforge.net/)}).
+    \item Machine learning \cite{scikit-learn} (\url{http://scikit-learn.org/});
+    \item Visualisation \cite{Hunter:2007} (\url{http://matplotlib.org/});
+    \item Mathematics \cite{sage} (\url{http://www.sagemath.org/});
+    \item Astrophysics \cite{astropy} (\url{http://www.astropy.org/});
+    \item Data manipulation \cite{mckinney-proc-scipy-2010} (\url{http://pandas.pydata.org/});
+    \item Algorithmic Game Theory \cite{Mckelvey06gambit:software} (\url{http://gambit.sourceforge.net/})).
 \end{itemize}

### 2016-03-10 tex/paper.tex

@@
     The Axelrod library is an open source Python package that allows for
-    reproducible game theoretic research into the iterated Prisoner's Dilemma.
+    reproducible game theoretic research into the Iterated Prisoner's Dilemma.
     This area of research began in the 1980s but suffers from a lack of
-    documented and test code. The goal of the library is to provide such
-    a resource, with facilities the design new strategies and interactions
-    between them, as well as conducting tournaments and ecological simulations
-    for population of strategies.
+    documentation and test code. The goal of the library is to provide such
+    a resource, with facilities for the design of new strategies and
+    interactions between them, as well as conducting tournaments and ecological
+    simulations for populations of strategies.
 
 \noindent
-    With a growing collection of 120 strategies the library is a also a platform
-    for an original tournament that in itself is of interest to the game
-    theoretic community.
+    With a growing collection of 120 strategies, the library is a also a
+    platform for an original tournament that, in itself, is of interest to the
+    game theoretic community.
 
 \noindent
-    This paper describes the iterated Prisoner's Dilemma, the Axelrod library
+    This paper describes the Iterated Prisoner's Dilemma, the Axelrod library
     and its development, and insights gained from some novel research.
@@
 
-Several iterated prisoner's dilemma tournaments have generated much interest,
+Several Iterated Prisoner's Dilemma tournaments have generated much interest;
 including Axelrod's original tournaments \cite{Axelrod1980a,Axelrod1980b},
 two 2004 anniversary tournaments (ref?), and
-the Stewart and Plotkin 2012 tournament \cite{Stewart2012} following the
+the Stewart and Plotkin 2012 tournament \cite{Stewart2012}, following the
 discovery of zero-determinant strategies.  Subsequent research has spawned an
@@
 well-known tournaments, in only one case is the full original source code
-available (Axelrod's second tournament \cite{Axelrod1980b}, in FORTRAN); in no
+available (Axelrod's second tournament \cite{Axelrod1980b}, in FORTRAN). In no
 cases is the available code well-documented, easily modifiable, or released with
@@
 strategies are not sufficiently described to enable reliable recreation
-(in the absense of source code), with \cite{slany2007some} being a notable
-counter-example. In some cases strategies are revised without updates to their
+(in the absence of source code), with \cite{slany2007some} being a notable
+counter-example. In some cases, strategies are revised without updates to their
 names or published implementations \cite{li2007design, li2011engineering}.
@@
     \item Extensive: 120 strategies are included, with infinitely-many
-    strategies available in the case of parameterized strategies
+        strategies available in the case of parametrised strategies
     \item Extensible: easy to modify to include new strategies and to run new tournaments
@@
 1980, Axelrod wrote two papers:~\cite{Axelrod1980a,Axelrod1980b} which
-describe a computer tournament that has been a imajor influence on
+describe a computer tournament that has been a major influence on
 subsequent game theoretic work~\cite{Banks1990, Bendor1991, Boyd1987, Chellapilla1999,
@@
 for details) where two players repeatedly play the normal form game of
-(\ref{equ:one-shot}) in full knowledge of each others playing history to date.
+(\ref{equ:one-shot}) in full knowledge of each other's playing history to date.
 An excellent description of the \textit{one shot} game is given
@@
 Furthermore, in \cite{Isaac2008} Python is described as an appropriate language for the
-reproduction of Iterated Prisoner's dilemma tournaments due to its object
+reproduction of Iterated Prisoner's Dilemma tournaments due to its object
 oriented nature and readability.
@@
 
-As stated in Section~\ref{sec:introduction} one of the main goals of the library
+As stated in Section~\ref{sec:introduction}, one of the main goals of the library
 is to allow for the easy contribution of strategies. Doing this requires the
@@
 Figure~\ref{fig:number_of_strategies_against_date}. Despite this, due to
-previous research being done in an irreproducible manner, with for example no
-source code, and/or vaguely described strategies, not all previous tournaments
-are yet to be reproduced. In fact, some of the early tournaments might be
+previous research being done in an irreproducible manner with, for example, no
+source code and/or vaguely described strategies, not all previous tournaments
+can yet be reproduced. In fact, some of the early tournaments might be
 impossible to reproduce as the source code is forever lost. This library aims
@@
 plays of the opponent to gain some information about its intentions whilst still
-taking in to account the recent play. The actual winning strategy is an instance
+taking into account the recent play. The actual winning strategy is an instance
 of the framework for \(m=n=2\) for which an evolutionary algorithm has been used
@@
 This paper has presented a game theoretic software package that aims to address
-reproducibility of research into the iterated prisoner's dilemma. The open
+reproducibility of research into the Iterated Prisoner's Dilemma. The open
 nature of the development of the library has lead rapidly to the inclusion of
@@
 
-The ability to readily have available a large number of strategies makes this
+The ability to have readily available a large number of strategies makes this
 tool an excellent and obvious example of the benefits of open research which

### 2016-03-10 tex/paper.tex
Adding missing reference and re-ordering.

@@
 including Axelrod's original tournaments \cite{Axelrod1980a,Axelrod1980b},
-two 2004 anniversary tournaments (ref?), and
+two 2004 anniversary tournaments \cite{kendall2007iterated}, and
 the Stewart and Plotkin 2012 tournament \cite{Stewart2012}, following the
@@
 theorem for repeated games \cite{Maschler2013}. This aspect of incomplete
-information is also considered in \cite{Molander1985, Bendor1991, Lee2015} where
+information is also considered in \cite{Bendor1991, Lee2015, Molander1985} where
 ``noisy'' tournaments randomly flip the choice made by a given strategy. In

### 2016-03-11 tex/paper.tex
Adding high school contributions.

@@
 
-To date the library has had contributions from 24 contributors from a variety
-of backgrounds. These contributions have both been in terms of strategies (one
-strategy is the creation of an undergraduate mathematics student with little
-prior knowledge of programming) as well as the architecture of the library
-itself. You can see an overview of the structure of the source code in
+To date the library has had contributions from 24 contributors from a variety of
+backgrounds. These contributions have been in terms of strategies. One strategy
+is the creation of an undergraduate mathematics student with little prior
+knowledge of programming. Two other strategies were written by a 15 year old
+secondary school student. As well as these strategy contributions, vital
+architectural improvements to the library itself have also been received. You
+can see an overview of the structure of the source code in
 Figure~\ref{fig:overview}.

### 2016-03-31 tex/paper.tex
2 -> multiple for HS contributions.
Adding authors.
Correct affiliation for Thomas.
Correct affiliation for James.
Prob end tournaments removed.

@@
 \usepackage{subcaption}  % Subfigures
+\usepackage{authblk}  % Authors
 
@@
 
-\author{Owen Campbell\\
-        \and
-        Marc Harper\\
-        \and
-        Vincent Knight\\
-        \and
-        Karol Langner\\
-}
+% Core devs (alphabetic order of last name)
+\author[1]{Owen Campbell}
+\author[1]{Mark Harper}
+\author[2]{Vincent Knight}
+\author[1]{Karol Langner}
+
+% All devs (alphabetic order of last name)
+\author[2]{James Campbell}
+\author[5]{Thomas Campbell}
+\author[2]{Alex Carney}
+\author[2]{Martin Chorley}
+\author[1]{Cameron Davidson-Pilon}
+\author[1]{Tom{\'a}{\v s} Ehrlich}
+\author[1]{Martin Jones}
+\author[4]{Georgios Koutsovoulos}
+\author[1]{Holly Marissa}
+\author[1]{Jochen M{\"u}ller}
+\author[2]{Geraint Palmer}
+\author[3]{Paul Slavin}
+\author[2]{Timothy Standen}
+\author[1]{Luis Visintini}
+\author[1]{Karl ?}
+
+% Affiliations
+\affil[1]{Not affiliated}
+\affil[2]{Cardiff University}
+\affil[3]{The University of Manchester}
+\affil[4]{The University of Edinburgh}
+\affil[5]{St. Nicholas Catholic High School, Hartford}
+
+% Corresponding author
 
@@
 \maketitle
+\begin{center}
+    \thanks{Corresponding author: Vincent Knight
+        \href{mailto:knightva@cf.ac.uk}{knightva@cf.ac.uk}}
+\end{center}
 
@@
 is the creation of an undergraduate mathematics student with little prior
-knowledge of programming. Two other strategies were written by a 15 year old
+knowledge of programming. Multiple other strategies were written by a 15 year old
 secondary school student. As well as these strategy contributions, vital
@@
     \item Noisy tournaments;
+    \item Tournaments with probabilistic ending of interactions;
     \item Ecological analysis of tournaments;
@@
 
-These capabilities are constantly being updated. Some immediate further work
-includes allowing for tournaments of probabilistic length as well as further
-implementation of known strategies.
+These capabilities are constantly being updated.
 

### 2016-03-31 tex/paper.tex
Updating the boxplot.

@@
         use and modification
-    \item Extensive: 120 strategies are included, with infinitely-many
+    \item Extensive: 123 strategies are included, with infinitely-many
         strategies available in the case of parametrised strategies
@@
 	\includegraphics[width=.9\textwidth]{../img/tournament.pdf}
-	\caption{Results from the library tournament (2016-02-10)}
+	\caption{Results from the library tournament (2016-03-31)}
 	\label{fig:tournament}
@@
 taking into account the recent play. The actual winning strategy is an instance
-of the framework for \(m=n=2\) for which an evolutionary algorithm has been used
-to train it.  More details of this can be found in \cite{Jones2015}. In
-\cite{Knight2015} experiments are described that evaluate how this particular
-strategy behaves in environments other than those in which it was trained and it
-continues to perform strongly.
+of the framework for \(m=n=2\) for which a particle swarm algorithm has been
+used to train it, the second placed strategy was trained with an evolutionary
+algorithms. More details of this can be found in \cite{Goerge2016, Jones2015}.
+In \cite{Knight2015} experiments are described that evaluate how the second
+placed strategy behaves in environments other than those in which it was trained
+and it continues to perform strongly.
 

### 2016-03-31 scripts/scrape_repo.py
Repeating scraping of repo.

@@ -5,6 +5,7 @@ Works with `number_of_strategies.py` to get the number of strategies in the
 library at each commit.
 """
 from git import Repo
+from tqdm import tqdm
 import os
 import subprocess
 
@@ -26,7 +27,7 @@ try:
 except OSError:
     pass
 
-for c in sorted(all_commits, key=lambda x:x.committed_date):
+for c in tqdm(sorted(all_commits, key=lambda x:x.committed_date)):
 
     for rubbish in [".DS_Store",
                     "axelrod/.DS_Store",

### 2016-04-01 tex/paper.tex
Swapping citation order.
Using jors style file.
Adding Kristian (my bad for forgetting).
Conflicts:
	tex/paper.pdf
Revert "Using jors style file."
This reverts commit 9d71034ace5ec1638b0d8982492c8b965cb3da5a.

Conflicts:
	tex/paper.pdf
Correct first two section names as per JORS.

@@
 \author[1]{Cameron Davidson-Pilon}
+\author[1]{Kristian Glass}
 \author[1]{Tom{\'a}{\v s} Ehrlich}
@@
 
-\section{Introduction}\label{sec:introduction}
+\section{Overview}\label{sec:sec:overview}
 
@@
 
+\section{Implementation and architecture}
+
 \subsection{Description of the Axelrod Python package}\label{sec:description-of-axelrod-python}
@@
 
-As stated in Section~\ref{sec:introduction}, one of the main goals of the library
+As stated in Section~\ref{sec:sec:overview}, one of the main goals of the library
 is to allow for the easy contribution of strategies. Doing this requires the
@@
 
-\section{New strategies, tournaments and implications}\label{sec:new-strategies-and-implications}
+\subsection{New strategies, tournaments and implications}\label{sec:new-strategies-and-implications}
 
@@
 used to train it, the second placed strategy was trained with an evolutionary
-algorithms. More details of this can be found in \cite{Goerge2016, Jones2015}.
+algorithms. More details of this can be found in \cite{Jones2015, George2016}.
 In \cite{Knight2015} experiments are described that evaluate how the second

### 2016-04-01 tex/paper.tex
Adding contributors list.

@@
 \usepackage{authblk}  % Authors
+
+\usepackage{multicol}
 
@@
 \author[1]{Luis Visintini}
-\author[1]{Karl ?}
+\author[1]{Karl Molden}
 
@@
 
+\begin{multicols}{3}
     \begin{enumerate}
@@
     \end{enumerate}
+\end{multicols}
 
@@
 
+\section{Availability}\label{sec:availability}
+
+\subsection{Operating system}
+
+The Axelrod library runs on all major operating systems: Linux, Mac OSX and
+Windows.
+
+\subsection{Programming language}
+
+The library is continuously tested for Python 2.7, 3.3, 3.4 and 3.5.
+
+\subsection{Additional system requirements}
+
+There are no specific additional system requirements.
+
+\subsection{Support}
+
+Support is readily available in multiple forms:
+
+\begin{itemize}
+    \item An online chat channel:
+        \url{https://gitter.im/Axelrod-Python/Axelrod}.
+    \item An  email group:
+        \url{https://groups.google.com/forum/#!topic/axelrod-python}.
+\end{itemize}
+
+\subsection{Dependencies}
+
+The following Python libraries are required dependencies:
+
+\begin{multicols}{3}
+    \begin{itemize}
+        \item Numpy 1.9.2:
+        \item Matplotlib 1.4.2:
+        \item Cloudpickle  0.1.1:
+        \item Hypothesis  3.0:
+        \item Testfixtures  4.9.1:
+    \end{itemize}
+\end{multicols}
+
+\subsection{List of contributors}
+
+The names of all the contributors are not known: as these were mainly done
+through github and certain have not provided their name or responded to a
+request for further details. Here is an incomplete list:
+
+\begin{multicols}{3}
+    \begin{itemize}
+        \item {Owen Campbell}
+        \item {Mark Harper}
+        \item {Vincent Knight}
+        \item {Karol Langner}
+        \item {James Campbell}
+        \item {Thomas Campbell}
+        \item {Alex Carney}
+        \item {Martin Chorley}
+        \item {Cameron Davidson-Pilon}
+        \item {Kristian Glass}
+        \item {Tom{\'a}{\v s} Ehrlich}
+        \item {Martin Jones}
+        \item {Georgios Koutsovoulos}
+        \item {Holly Marissa}
+        \item {Jochen M{\"u}ller}
+        \item {Geraint Palmer}
+        \item {Paul Slavin}
+        \item {Timothy Standen}
+        \item {Luis Visintini}
+        \item {Karl Molden}
+        \item {Jason Young}
+        \item {Andy Boot}
+        \item {Anna Barriscale}
+    \end{itemize}
+\end{multicols}
+
+\subsection{Archive}
+\subsection{Code repository}
+
+\section{Reuse potential}\label{sec:reuse}
+
 \section{Conclusion}\label{sec:conclusion}

### 2016-04-01 tex/paper.tex
Adding a reuse section

@@
 The names of all the contributors are not known: as these were mainly done
-through github and certain have not provided their name or responded to a
+through Github and certain have not provided their name or responded to a
 request for further details. Here is an incomplete list:
@@
 \subsection{Archive}
+
+\begin{multicols}{2}
+    \begin{itemize}
+        \item Name: Zenodo
+        \item Persistent identifier:
+\href{https://zenodo.org/record/45187}{10.5281/zenodo.45187}
+        \item Licence: MIT
+        \item Publisher:  Vincent Knight
+        \item Version published: Axelrod: Alternator Release. v0.0.28
+        \item Date published: 2016-01-26
+    \end{itemize}
+\end{multicols}
+
 \subsection{Code repository}
 
+\begin{multicols}{2}
+    \begin{itemize}
+        \item Name: Github
+        \item Identifier: \url{https://github.com/Axelrod-Python/Axelrod}
+        \item Licence: MIT
+        \item Date published: 2015-02-16
+    \end{itemize}
+\end{multicols}
+
 \section{Reuse potential}\label{sec:reuse}
+
+The Axelrod library has been designed with sustainable software practice in
+mind. There is an extensive documentation suite:
+\url{axelrod.readthedocs.org/en/latest/}. Furthermore, there is a growing set
+of example Jupyter notebooks available here:
+\url{https://github.com/Axelrod-Python/Axelrod-notebooks}.
+
+This library has the potential to be a common standard for research in to the
+iterated Prisoner's dilemma. In particular, having a large library of
+tested strategies readily available for experimentation is of high value to the
+research community.
+
+This has been evidenced by the work described in
+Section~\ref{sec:new-strategies-and-implications} the library has already shown
+it's potential for reuse.
 

### 2016-04-01 tex/paper.tex
Resizing images to reduce page count.

@@
 		\centering
-		\includegraphics[width=\textwidth]{../img/demo_tournament.pdf}
+		\includegraphics[width=.75\textwidth]{../img/demo_tournament.pdf}
 		\caption{The results from a simple tournament.}
@@
 		\centering
-		\includegraphics[width=\textwidth]{../img/stewart_tournament.pdf}
+		\includegraphics[width=.75\textwidth]{../img/stewart_tournament.pdf}
 		\caption{The results from \cite{Stewart2012}.}
@@
 		\centering
-		\includegraphics[width=\textwidth]{../img/outline_of_library.pdf}
+		\includegraphics[width=.75\textwidth]{../img/outline_of_library.pdf}
 		\caption{An overview of the source code.}
@@
 		\centering
-		\includegraphics[width=\textwidth]{../img/number_of_strategies_with_arima_projection.pdf}
+		\includegraphics[width=.9\textwidth]{../img/number_of_strategies_with_arima_projection.pdf}
 		\caption{The number of strategies included in the library}
@@
 	\centering
-	\includegraphics[width=.9\textwidth]{../img/tournament.pdf}
+	\includegraphics[width=.75\textwidth]{../img/tournament.pdf}
 	\caption{Results from the library tournament (2016-03-31)}

### 2016-04-01 tex/paper.tex
"Using jors style file."
This reverts commit 1905b29443dc541fa16dedd80d2c20ec0b09f9b9.

Conflicts:
	tex/paper.pdf
Complete jors styling.

@@
-\documentclass{article}
+\documentclass{jors}
+
+%% Set the header information
+
+% Commenting out as this overrides the section titles.
+%\pagestyle{fancy}
+%\definecolor{mygray}{gray}{0.6}
+%\renewcommand\headrule{}
+%\rhead{\footnotesize 3}
+%\rhead{\textcolor{gray}{UP JORS software Latex paper template version 0.1}}
 
@@
 
-% Lazy page formating (we can adjust when submitting)
-\usepackage{fullpage}
-\usepackage[parfill]{parskip}
-%-----------------------------
-
 \usepackage{amsmath}  % Basic
+\usepackage{booktabs}  % Better tables
+\usepackage{graphicx}  % Images
 \usepackage{hyperref}  % Links etc
-\usepackage{booktabs}  % Better tables
 \usepackage{minted}  % Code
-\usepackage{graphicx}  % Images
+\usepackage{multicol}  % Multi column list
 \usepackage{subcaption}  % Subfigures
-\usepackage{authblk}  % Authors
-
-\usepackage{multicol}
-
-\title{An open reproducible framework for the study of the iterated prisoner's
-dilemma}
-
-% Core devs (alphabetic order of last name)
-\author[1]{Owen Campbell}
-\author[1]{Mark Harper}
-\author[2]{Vincent Knight}
-\author[1]{Karol Langner}
-
-% All devs (alphabetic order of last name)
-\author[2]{James Campbell}
-\author[5]{Thomas Campbell}
-\author[2]{Alex Carney}
-\author[2]{Martin Chorley}
-\author[1]{Cameron Davidson-Pilon}
-\author[1]{Kristian Glass}
-\author[1]{Tom{\'a}{\v s} Ehrlich}
-\author[1]{Martin Jones}
-\author[4]{Georgios Koutsovoulos}
-\author[1]{Holly Marissa}
-\author[1]{Jochen M{\"u}ller}
-\author[2]{Geraint Palmer}
-\author[3]{Paul Slavin}
-\author[2]{Timothy Standen}
-\author[1]{Luis Visintini}
-\author[1]{Karl Molden}
-
-% Affiliations
-\affil[1]{Not affiliated}
-\affil[2]{Cardiff University}
-\affil[3]{The University of Manchester}
-\affil[4]{The University of Edinburgh}
-\affil[5]{St. Nicholas Catholic High School, Hartford}
-
-% Corresponding author
-
-\date{\today}
 
 \begin{document}
+%% Set the header information
+\pagestyle{fancy}
+\definecolor{mygray}{gray}{0.6}
+\renewcommand\headrule{}
+\rhead{\footnotesize 3}
+\rhead{\textcolor{gray}{UP JORS software Latex paper template version 0.1}}
 
-\maketitle
-\begin{center}
-    \thanks{Corresponding author: Vincent Knight
-        \href{mailto:knightva@cf.ac.uk}{knightva@cf.ac.uk}}
-\end{center}
+\rule{\textwidth}{1pt}
 
-\begin{abstract}
-\noindent
+\section*{(1) Overview}\label{sec:sec:overview}
+
+\vspace{0.5cm}
+
+\section*{Title}
+
+An open reproducible framework for the study of the iterated prisoner's
+dilemma.
+
+\section*{Authors}
+
+\begin{multicols}{2}
+    \begin{enumerate}[noitemsep,topsep=0pt]
+        % Core devs (alphabetic order of last name)
+        \item Campbell, Owen
+        \item Harper, Marc
+        \item Knight, Vincent
+        \item Langner, Karol
+        % All devs (alphabetic order of last name)
+        \item Campbell, James
+        \item Campbell, Thomas
+        \item Carney, Alex
+        \item Chorley, Martin
+        \item Davidson-Pilon, Cameron
+        \item Glass, Kristian
+        \item Ehrlich Tom{\'a}{\v s}
+        \item Jones, Martin
+        \item Koutsovoulos, Georgios
+        \item Marissa, Holly
+        \item M{\"u}ller, Jochen
+        \item Palmer, Geraint
+        \item Slavin, Paul
+        \item Standen, Timothy
+        \item Visintini, Luis
+        \item Molden, Karl
+    \end{enumerate}
+\end{multicols}
+
+\section*{Paper Author Roles and Affiliations}
+
+\begin{multicols}{2}
+    \begin{enumerate}[noitemsep,topsep=0pt]
+\item Development; Not affiliated
+\item Development; Not affiliated
+\item Development; Knight, Vincent
+\item Development; Cardiff University
+\item Development; Cardiff University
+\item Development; St. Nicholas Catholic High School, Hartford
+\item Development; Cardiff University
+\item Development; Cardiff University
+\item Development; Not affiliated
+\item Development; Not affiliated
+\item Development; Not affiliated
+\item Development; Not affiliated
+\item Development; The University of Edinburgh
+\item Development; Not affiliated
+\item Development; Not affiliated
+\item Development; Not affiliated
+\item Development; The University of Manchester
+\item Development; Cardiff University
+\item Development; Not affiliated
+\item Development; Not affiliated
+    \end{enumerate}
+\end{multicols}
+
+\section*{Abstract}
+
 The Axelrod library is an open source Python package that allows for
@@
 
-\noindent
 With a growing collection of 120 strategies, the library is a also a
@@
 
-\noindent
 This paper describes the Iterated Prisoner's Dilemma, the Axelrod library
 and its development, and insights gained from some novel research.
-\end{abstract}
 
-\section{Overview}\label{sec:sec:overview}
+\section*{Keywords}
+
+Game Theory; Prisoners Dilemma; Python
+
+\section*{Introduction}
 
@@
 
-\begin{itemize}
+\begin{itemize}[noitemsep,topsep=0pt]
     \item To enable the reproduction of Iterated Prisoner's Dilemma
@@
 
-\begin{itemize}
+\begin{itemize}[noitemsep,topsep=0pt]
     \item Open: all code is released under an MIT license;
@@
 
-Before describing the package in more detail in
-Section~\ref{sec:description-of-axelrod-python}, an overview of some previous
-Iterated Prisoner's Dilemma research will be given in
-Section~\ref{sec:review}. Section~\ref{sec:new-strategies-and-implications} will
-describe some early research and a conclusion is offered in
-Section~\ref{sec:conclusion}.
-
-\subsection{Review of the literature}\label{sec:review}
+\section*{Review of the literature}\label{sec:review}
 
@@
 The tournament is based on an iterated game (see~\cite{Maschler2013} or similar
-for details) where two players repeatedly play the normal form game of
-(\ref{equ:one-shot}) in full knowledge of each other's playing history to date.
-An excellent description of the \textit{one shot} game is given
+for details) where two players repeatedly play the normal form game
+of~(\ref{equ:one-shot}) in full knowledge of each other's playing history to
+date.  An excellent description of the \textit{one shot} game is given
 in~\cite{Gotts2003} which is paraphrased below:
@@
 
-\begin{itemize}
+\begin{itemize}[noitemsep,topsep=0pt]
     \item If both choose \(C\), they receive a payoff of \(R\)
@@
 
-The game of (\ref{equ:one-shot}) is called the Prisoner's Dilemma. Specific
+The game of~(\ref{equ:one-shot}) is called the Prisoner's Dilemma. Specific
 numerical values of \((R,S,T,P)=(3,0,5,1)\) are often used in the literature,
-although any satisfying the conditions in \ref{equ:one-shot} will yield similar
+although any satisfying the conditions in~\ref{equ:one-shot} will yield similar
 results.  Axelrod's tournaments (and further implementations of these) are
@@
 
-\section{Implementation and architecture}
+\section*{Implementation and architecture}
 
-\subsection{Description of the Axelrod Python package}\label{sec:description-of-axelrod-python}
+\section*{Description of the Axelrod Python package}\label{sec:description-of-axelrod-python}
 
@@
 
-\begin{itemize}
+\begin{itemize}[noitemsep,topsep=0pt]
+    \item Algorithmic Game Theory \cite{Mckelvey06gambit:software}
+          (\url{http://gambit.sourceforge.net/})).
+    \item Astrophysics \cite{astropy} (\url{http://www.astropy.org/});
+    \item Data manipulation \cite{mckinney-proc-scipy-2010}
+          (\url{http://pandas.pydata.org/});
     \item Machine learning \cite{scikit-learn} (\url{http://scikit-learn.org/});
+    \item Mathematics \cite{sage} (\url{http://www.sagemath.org/});
     \item Visualisation \cite{Hunter:2007} (\url{http://matplotlib.org/});
-    \item Mathematics \cite{sage} (\url{http://www.sagemath.org/});
-    \item Astrophysics \cite{astropy} (\url{http://www.astropy.org/});
-    \item Data manipulation \cite{mckinney-proc-scipy-2010} (\url{http://pandas.pydata.org/});
-    \item Algorithmic Game Theory \cite{Mckelvey06gambit:software} (\url{http://gambit.sourceforge.net/})).
 \end{itemize}
@@
 
-As stated in Section~\ref{sec:sec:overview}, one of the main goals of the library
+As stated in the Overview, one of the main goals of the library
 is to allow for the easy contribution of strategies. Doing this requires the
@@
 
-Section~\ref{sec:new-strategies-and-implications} will describe in more detail
-some of research capabilities of the library.
-
-\subsection{New strategies, tournaments and implications}\label{sec:new-strategies-and-implications}
+\section*{New strategies, tournaments and implications}\label{sec:new-strategies-and-implications}
 
@@
 
-\begin{multicols}{3}
-    \begin{enumerate}
+\begin{multicols}{2}
+    \begin{enumerate}[noitemsep,topsep=0pt]
         \item Cooperator
@@
 
-\begin{itemize}
+\begin{itemize}[noitemsep,topsep=0pt]
     \item A closer look at zero determinant strategies, showing that
@@
 
-\section{Availability}\label{sec:availability}
+\section*{(2) Availability}\label{sec:availability}
 
-\subsection{Operating system}
+\section*{Operating system}
 
@@
 
-\subsection{Programming language}
+\section*{Programming language}
 
@@
 
-\subsection{Additional system requirements}
+\section*{Additional system requirements}
 
@@
 
-\subsection{Support}
+\section*{Support}
 
@@
 
-\begin{itemize}
+\begin{itemize}[noitemsep,topsep=0pt]
     \item An online chat channel:
@@
 
-\subsection{Dependencies}
+\section*{Dependencies}
 
@@
 \begin{multicols}{3}
-    \begin{itemize}
+    \begin{itemize}[noitemsep,topsep=0pt]
         \item Numpy 1.9.2:
@@
 
-\subsection{List of contributors}
+\section*{List of contributors}
 
@@
 
-\begin{multicols}{3}
-    \begin{itemize}
+\begin{multicols}{2}
+    \begin{itemize}[noitemsep,topsep=0pt]
         \item {Owen Campbell}
@@
 
-\subsection{Archive}
+\section*{Software location:}
 
-\begin{multicols}{2}
-    \begin{itemize}
-        \item Name: Zenodo
-        \item Persistent identifier:
+{\bf Archive}
+
+\begin{description}[noitemsep,topsep=0pt]
+    \item[Name:] Zenodo
+    \item[Persistent identifier:]
 \href{https://zenodo.org/record/45187}{10.5281/zenodo.45187}
-        \item Licence: MIT
-        \item Publisher:  Vincent Knight
-        \item Version published: Axelrod: Alternator Release. v0.0.28
-        \item Date published: 2016-01-26
-    \end{itemize}
-\end{multicols}
+    \item[Licence:] MIT
+    \item[Publisher:]  Vincent Knight
+    \item[Version published:] Axelrod: Alternator Release. v0.0.28
+    \item[Date published:] 2016-01-26
+\end{description}
 
-\subsection{Code repository}
+{\bf Code repository}
 
-\begin{multicols}{2}
-    \begin{itemize}
-        \item Name: Github
-        \item Identifier: \url{https://github.com/Axelrod-Python/Axelrod}
-        \item Licence: MIT
-        \item Date published: 2015-02-16
-    \end{itemize}
-\end{multicols}
+\begin{description}[noitemsep,topsep=0pt]
+    \item[Name:] Github
+    \item[Identifier:] \url{https://github.com/Axelrod-Python/Axelrod}
+    \item[Licence:] MIT
+    \item[Date published:] 2015-02-16
+\end{description}
 
-\section{Reuse potential}\label{sec:reuse}
+\section*{Reuse potential}\label{sec:reuse}
 
@@
 
-This has been evidenced by the work described in
-Section~\ref{sec:new-strategies-and-implications} the library has already shown
+This has been evidenced by the work described: the library has already shown
 it's potential for reuse.
 
-\section{Conclusion}\label{sec:conclusion}
+\section*{Conclusion}\label{sec:conclusion}
 
@@
 
-\begin{itemize}
+\begin{itemize}[noitemsep,topsep=0pt]
     \item Noisy tournaments;

### 2016-04-01 tex/paper.tex
Putting myself first in the list (as corresponding)
Remove back refs in bibliography.
Final checks and adding acknowledgements etc.

@@
 % Nicer bibliography management
-\usepackage[backend=biber, backref=true, firstinits=true, url=true, isbn=true]{biblatex}
+\usepackage[backend=biber, firstinits=true, url=true, isbn=true]{biblatex}
 \addbibresource{references.bib}
@@
     \begin{enumerate}[noitemsep,topsep=0pt]
-        % Core devs (alphabetic order of last name)
+        % Core devs (alphabetic order of last name after Vince as corresponding
+        % goes first).
+        \item Knight, Vincent
         \item Campbell, Owen
         \item Harper, Marc
-        \item Knight, Vincent
         \item Langner, Karol
@@
 
-With a growing collection of 120 strategies, the library is a also a
+With a growing collection of 122 strategies, the library is a also a
 platform for an original tournament that, in itself, is of interest to the
@@
 
-As stated in the Overview, one of the main goals of the library
+As stated in the \textbf{Introduction}, one of the main goals of the library
 is to allow for the easy contribution of strategies. Doing this requires the
@@
 
-To date the library has had contributions from 24 contributors from a variety of
-backgrounds. These contributions have been in terms of strategies. One strategy
-is the creation of an undergraduate mathematics student with little prior
-knowledge of programming. Multiple other strategies were written by a 15 year old
-secondary school student. As well as these strategy contributions, vital
-architectural improvements to the library itself have also been received. You
-can see an overview of the structure of the source code in
-Figure~\ref{fig:overview}.
+To date the library has had contributions from 24 contributors from a variety
+of backgrounds. These contributions have been in terms of strategies. One
+strategy is the creation of an undergraduate mathematics student with little
+prior knowledge of programming. Multiple other strategies were written by a 15
+year old secondary school student. Both of these students are authors of this
+paper. As well as these strategy contributions, vital architectural
+improvements to the library itself have also been received. You can see an
+overview of the structure of the source code in Figure~\ref{fig:overview}.
 
@@
 
-This library has the potential to be a common standard for research in to the
-iterated Prisoner's dilemma. In particular, having a large library of
-tested strategies readily available for experimentation is of high value to the
-research community.
-
+The ability to have readily available a large number of strategies makes this
+tool an excellent and obvious example of the benefits of open research which
+should positively impact the game theoretic community.
 This has been evidenced by the work described: the library has already shown
@@
 
-\section*{Conclusion}\label{sec:conclusion}
+\section*{Conclusion}
 
@@
 
-The ability to have readily available a large number of strategies makes this
-tool an excellent and obvious example of the benefits of open research which
-should positively impact the game theoretic community.
+\section*{Acknowledgements}
+
+The authors would like to thank all contributors. Also, they thank
+Robert Axelrod himself for his well wishes with the library.
+
+\section*{Competing interests}
+
+The authors declare that they have no competing interests.
 

### 2016-04-01 tex/paper.tex
Removing doctest.

@@
 >>> plot = axelrod.Plot(results)
->>> plot.boxplot()  # doctest:+SKIP
+>>> plot.boxplot()
     \end{minted}

### 2016-04-04 tex/paper.tex
Adding reference to hypothesis.
Correct Marissa name and affiliation fix
Correct name for Marissa!!!
Correct correct name...
The name might actually be correct now...
Moving files.

@@
         \item Koutsovoulos, Georgios
-        \item Marissa, Holly
+        \item Tibble, Holly
         \item M{\"u}ller, Jochen
@@
     \begin{enumerate}[noitemsep,topsep=0pt]
+\item Development; Cardiff University
 \item Development; Not affiliated
 \item Development; Not affiliated
-\item Development; Knight, Vincent
-\item Development; Cardiff University
+\item Development; Not affiliated
 \item Development; Cardiff University
@@
     \item Reproducible and well-tested: at the time of writing there is an excellent level of
-        integrated tests with 99.37\% coverage
+        integrated tests with 99.37\% coverage (including property based tests:
+        \cite{Hypothesis3.0.3}
     \item Well-documented: all features of the library are documented for ease of
@@
 		\centering
-		\includegraphics[width=.75\textwidth]{../img/demo_tournament.pdf}
+		\includegraphics[width=.75\textwidth]{demo_tournament.pdf}
 		\caption{The results from a simple tournament.}
@@
 		\centering
-		\includegraphics[width=.75\textwidth]{../img/stewart_tournament.pdf}
+		\includegraphics[width=.75\textwidth]{stewart_tournament.pdf}
 		\caption{The results from \cite{Stewart2012}.}
@@
 		\centering
-		\includegraphics[width=.75\textwidth]{../img/outline_of_library.pdf}
+		\includegraphics[width=.75\textwidth]{outline_of_library.pdf}
 		\caption{An overview of the source code.}
@@
 		\centering
-		\includegraphics[width=.9\textwidth]{../img/number_of_strategies_with_arima_projection.pdf}
+		\includegraphics[width=.9\textwidth]{number_of_strategies_with_arima_projection.pdf}
 		\caption{The number of strategies included in the library}
@@
 	\centering
-	\includegraphics[width=.75\textwidth]{../img/tournament.pdf}
+	\includegraphics[width=.75\textwidth]{tournament.pdf}
 	\caption{Results from the library tournament (2016-03-31)}
@@
         \item {Georgios Koutsovoulos}
-        \item {Holly Marissa}
+        \item {Marissa Tibble}
         \item {Jochen M{\"u}ller}

### 2016-04-04 tex/paper.tex
Adding verbatim code highlighting.

@@
 \usepackage{hyperref}  % Links etc
-\usepackage{minted}  % Code
+% \usepackage{minted}  % Code: minted does not compile on arXiv
 \usepackage{multicol}  % Multi column list
@@
 \begin{figure}[!hbtp]
-    \begin{minted}[linenos, frame=lines]{python}
+    \begin{verbatim}
 >>> import axelrod
@@
 >>> plot.boxplot()
-    \end{minted}
+    \end{verbatim}
     \caption{A simple set of commands to create a demonstration tournament. The
@@
 \begin{figure}[!hbtp]
-    \begin{minted}[linenos, frame=lines]{python}
+    \begin{verbatim}
 class Grudger(Player):
@@
         return C
-    \end{minted}
+    \end{verbatim}
     \caption{Source code for the Grudger strategy.}
@@
 \begin{figure}[!hbtp]
-    \begin{minted}[linenos, frame=lines]{python}
+    \begin{verbatim}
 class TestGrudger(TestPlayer):
@@
         self.responses_test([C, C, D, D, D], [C, D, C, C, C], [D])
-    \end{minted}
+    \end{verbatim}
     \caption{Test code for the Grudger strategy.}
@@
 >>> plot.boxplot()
-    \end{minted}
+    \end{verbatim}
     \caption{Source code for reproducing the tournament of \cite{Stewart2012}}

### 2016-04-06 tex/paper.tex
Correct bib compilation for the Arxiv.
Correct affiliation for Geraint.
2nd modification:
- Adding references to multiprocess
- Typo found by Geraint

@@
 % Commenting out as this overrides the section titles.
-%\pagestyle{fancy}
-%\definecolor{mygray}{gray}{0.6}
-%\renewcommand\headrule{}
-%\rhead{\footnotesize 3}
-%\rhead{\textcolor{gray}{UP JORS software Latex paper template version 0.1}}
+\pagestyle{fancy}
+\definecolor{mygray}{gray}{0.6}
+\renewcommand\headrule{}
+\rhead{\footnotesize 3}
+\rhead{\textcolor{gray}{UP JORS software Latex paper template version 0.1}}
 
 % Nicer bibliography management
-\usepackage[backend=biber, firstinits=true, url=true, isbn=true]{biblatex}
+\usepackage[backend=bibtex, firstinits=true, url=true, isbn=true]{biblatex}
 \addbibresource{references.bib}
@@
 \item Development; Not affiliated
-\item Development; Not affiliated
+\item Development; Cardiff University
 \item Development; The University of Manchester
@@
         R,R & S,T\\
-        S,S & P,P
+        T,S & P,P
     \end{pmatrix}\quad\text{such that } T>R>P>S \text{ and } 2R > T + S
@@
 \begin{itemize}[noitemsep,topsep=0pt]
-    \item Noisy tournaments;
-    \item Tournaments with probabilistic ending of interactions;
-    \item Ecological analysis of tournaments;
-    \item Morality metrics based on \cite{Singer-Clark2014};
+    \item Noisy tournaments.
+    \item Tournaments with probabilistic ending of interactions.
+    \item Ecological analysis of tournaments.
+    \item Morality metrics based on \cite{Singer-Clark2014}.
     \item Transformation of strategies (in effect giving an infinite number of
-        strategies);
+        strategies).
     \item Classification of strategies according to multiple dimensions.
     \item Gathering of full interaction history for all interactions.
+    \item Parallelization of computations for tournaments with a high
+        computational cost \cite{Pathos, Mckerns2011}.
 \end{itemize}
@@
 \printbibliography
+%\bibliographystyle{plain}
+%\bibliography{references.bib}
 \end{document}

### 2016-04-12 tex/paper.tex
Update my name and affiliation

--- 2016-04-04 tex/paper.tex
@@
-\documentclass{jors}
-
-%% Set the header information
-
-% Commenting out as this overrides the section titles.
-%\pagestyle{fancy}
-%\definecolor{mygray}{gray}{0.6}
-%\renewcommand\headrule{}
-%\rhead{\footnotesize 3}
-%\rhead{\textcolor{gray}{UP JORS software Latex paper template version 0.1}}
+\documentclass{article}
 
 % Nicer bibliography management
-\usepackage[backend=biber, firstinits=true, url=true, isbn=true]{biblatex}
+\usepackage[backend=biber, backref=true, firstinits=true, url=true, isbn=true]{biblatex}
 \addbibresource{references.bib}
@@
 
+% Lazy page formating (we can adjust when submitting)
+\usepackage{fullpage}
+\usepackage[parfill]{parskip}
+%-----------------------------
+
 \usepackage{amsmath}  % Basic
+\usepackage{hyperref}  % Links etc
 \usepackage{booktabs}  % Better tables
+\usepackage{minted}  % Code
 \usepackage{graphicx}  % Images
-\usepackage{hyperref}  % Links etc
-\usepackage{minted}  % Code
-\usepackage{multicol}  % Multi column list
 \usepackage{subcaption}  % Subfigures
+\usepackage{authblk}  % Authors
+
+\title{An open reproducible framework for the study of the iterated prisoner's
+dilemma}
+
+% Core devs (alphabetic order of last name)
+\author[1]{Owen Campbell}
+\author[1]{Mark Harper}
+\author[2]{Vincent Knight}
+\author[6]{Karol M. Langner}
+
+% All devs (alphabetic order of last name)
+\author[2]{James Campbell}
+\author[5]{Thomas Campbell}
+\author[2]{Alex Carney}
+\author[2]{Martin Chorley}
+\author[1]{Cameron Davidson-Pilon}
+\author[1]{Kristian Glass}
+\author[1]{Tom{\'a}{\v s} Ehrlich}
+\author[1]{Martin Jones}
+\author[4]{Georgios Koutsovoulos}
+\author[1]{Holly Marissa}
+\author[1]{Jochen M{\"u}ller}
+\author[2]{Geraint Palmer}
+\author[3]{Paul Slavin}
+\author[2]{Timothy Standen}
+\author[1]{Luis Visintini}
+\author[1]{Karl ?}
+
+% Affiliations
+\affil[1]{Not affiliated}
+\affil[2]{Cardiff University}
+\affil[3]{The University of Manchester}
+\affil[4]{The University of Edinburgh}
+\affil[5]{St. Nicholas Catholic High School, Hartford}
+\affil[6]{Google Inc., Mountain View, CA}
+
+% Corresponding author
+
+\date{\today}
 
 \begin{document}
-%% Set the header information
-\pagestyle{fancy}
-\definecolor{mygray}{gray}{0.6}
-\renewcommand\headrule{}
-\rhead{\footnotesize 3}
-\rhead{\textcolor{gray}{UP JORS software Latex paper template version 0.1}}
 
-\rule{\textwidth}{1pt}
+\maketitle
+\begin{center}
+    \thanks{Corresponding author: Vincent Knight
+        \href{mailto:knightva@cf.ac.uk}{knightva@cf.ac.uk}}
+\end{center}
 
-\section*{(1) Overview}\label{sec:sec:overview}
-
-\vspace{0.5cm}
-
-\section*{Title}
-
-An open reproducible framework for the study of the iterated prisoner's
-dilemma.
-
-\section*{Authors}
-
-\begin{multicols}{2}
-    \begin{enumerate}[noitemsep,topsep=0pt]
-        % Core devs (alphabetic order of last name after Vince as corresponding
-        % goes first).
-        \item Knight, Vincent
-        \item Campbell, Owen
-        \item Harper, Marc
-        \item Langner, Karol
-        % All devs (alphabetic order of last name)
-        \item Campbell, James
-        \item Campbell, Thomas
-        \item Carney, Alex
-        \item Chorley, Martin
-        \item Davidson-Pilon, Cameron
-        \item Glass, Kristian
-        \item Ehrlich Tom{\'a}{\v s}
-        \item Jones, Martin
-        \item Koutsovoulos, Georgios
-        \item Tibble, Holly
-        \item M{\"u}ller, Jochen
-        \item Palmer, Geraint
-        \item Slavin, Paul
-        \item Standen, Timothy
-        \item Visintini, Luis
-        \item Molden, Karl
-    \end{enumerate}
-\end{multicols}
-
-\section*{Paper Author Roles and Affiliations}
-
-\begin{multicols}{2}
-    \begin{enumerate}[noitemsep,topsep=0pt]
-\item Development; Cardiff University
-\item Development; Not affiliated
-\item Development; Not affiliated
-\item Development; Not affiliated
-\item Development; Cardiff University
-\item Development; St. Nicholas Catholic High School, Hartford
-\item Development; Cardiff University
-\item Development; Cardiff University
-\item Development; Not affiliated
-\item Development; Not affiliated
-\item Development; Not affiliated
-\item Development; Not affiliated
-\item Development; The University of Edinburgh
-\item Development; Not affiliated
-\item Development; Not affiliated
-\item Development; Not affiliated
-\item Development; The University of Manchester
-\item Development; Cardiff University
-\item Development; Not affiliated
-\item Development; Not affiliated
-    \end{enumerate}
-\end{multicols}
-
-\section*{Abstract}
-
+\begin{abstract}
+\noindent
     The Axelrod library is an open source Python package that allows for
@@
 
-With a growing collection of 122 strategies, the library is a also a
+\noindent
+    With a growing collection of 120 strategies, the library is a also a
     platform for an original tournament that, in itself, is of interest to the
@@
 
+\noindent
     This paper describes the Iterated Prisoner's Dilemma, the Axelrod library
     and its development, and insights gained from some novel research.
+\end{abstract}
 
-\section*{Keywords}
-
-Game Theory; Prisoners Dilemma; Python
-
-\section*{Introduction}
+\section{Introduction}\label{sec:introduction}
 
@@
 
-\begin{itemize}[noitemsep,topsep=0pt]
+\begin{itemize}
     \item To enable the reproduction of Iterated Prisoner's Dilemma
@@
 
-\begin{itemize}[noitemsep,topsep=0pt]
+\begin{itemize}
     \item Open: all code is released under an MIT license;
     \item Reproducible and well-tested: at the time of writing there is an excellent level of
-        integrated tests with 99.37\% coverage (including property based tests:
-        \cite{Hypothesis3.0.3}
+        integrated tests with 99.37\% coverage
     \item Well-documented: all features of the library are documented for ease of
@@
 
-\section*{Review of the literature}\label{sec:review}
+Before describing the package in more detail in
+Section~\ref{sec:description-of-axelrod-python}, an overview of some previous
+Iterated Prisoner's Dilemma research will be given in
+Section~\ref{sec:review}. Section~\ref{sec:new-strategies-and-implications} will
+describe some early research and a conclusion is offered in
+Section~\ref{sec:conclusion}.
+
+\subsection{Review of the literature}\label{sec:review}
 
@@
 The tournament is based on an iterated game (see~\cite{Maschler2013} or similar
-for details) where two players repeatedly play the normal form game
-of~(\ref{equ:one-shot}) in full knowledge of each other's playing history to
-date.  An excellent description of the \textit{one shot} game is given
+for details) where two players repeatedly play the normal form game of
+(\ref{equ:one-shot}) in full knowledge of each other's playing history to date.
+An excellent description of the \textit{one shot} game is given
 in~\cite{Gotts2003} which is paraphrased below:
@@
 
-\begin{itemize}[noitemsep,topsep=0pt]
+\begin{itemize}
     \item If both choose \(C\), they receive a payoff of \(R\)
@@
 
-The game of~(\ref{equ:one-shot}) is called the Prisoner's Dilemma. Specific
+The game of (\ref{equ:one-shot}) is called the Prisoner's Dilemma. Specific
 numerical values of \((R,S,T,P)=(3,0,5,1)\) are often used in the literature,
-although any satisfying the conditions in~\ref{equ:one-shot} will yield similar
+although any satisfying the conditions in \ref{equ:one-shot} will yield similar
 results.  Axelrod's tournaments (and further implementations of these) are
@@
 
-\section*{Implementation and architecture}
-
-\section*{Description of the Axelrod Python package}\label{sec:description-of-axelrod-python}
+\subsection{Description of the Axelrod Python package}\label{sec:description-of-axelrod-python}
 
@@
 
-\begin{itemize}[noitemsep,topsep=0pt]
-    \item Algorithmic Game Theory \cite{Mckelvey06gambit:software}
-          (\url{http://gambit.sourceforge.net/})).
+\begin{itemize}
+    \item Machine learning \cite{scikit-learn} (\url{http://scikit-learn.org/});
+    \item Visualisation \cite{Hunter:2007} (\url{http://matplotlib.org/});
+    \item Mathematics \cite{sage} (\url{http://www.sagemath.org/});
     \item Astrophysics \cite{astropy} (\url{http://www.astropy.org/});
-    \item Data manipulation \cite{mckinney-proc-scipy-2010}
-          (\url{http://pandas.pydata.org/});
-    \item Machine learning \cite{scikit-learn} (\url{http://scikit-learn.org/});
-    \item Mathematics \cite{sage} (\url{http://www.sagemath.org/});
-    \item Visualisation \cite{Hunter:2007} (\url{http://matplotlib.org/});
+    \item Data manipulation \cite{mckinney-proc-scipy-2010} (\url{http://pandas.pydata.org/});
+    \item Algorithmic Game Theory \cite{Mckelvey06gambit:software} (\url{http://gambit.sourceforge.net/})).
 \end{itemize}
@@
 		\centering
-		\includegraphics[width=.75\textwidth]{demo_tournament.pdf}
+		\includegraphics[width=\textwidth]{../img/demo_tournament.pdf}
 		\caption{The results from a simple tournament.}
@@
 		\centering
-		\includegraphics[width=.75\textwidth]{stewart_tournament.pdf}
+		\includegraphics[width=\textwidth]{../img/stewart_tournament.pdf}
 		\caption{The results from \cite{Stewart2012}.}
@@
 
-As stated in the \textbf{Introduction}, one of the main goals of the library
+As stated in Section~\ref{sec:introduction}, one of the main goals of the library
 is to allow for the easy contribution of strategies. Doing this requires the
@@
 
-To date the library has had contributions from 24 contributors from a variety
-of backgrounds. These contributions have been in terms of strategies. One
-strategy is the creation of an undergraduate mathematics student with little
-prior knowledge of programming. Multiple other strategies were written by a 15
-year old secondary school student. Both of these students are authors of this
-paper. As well as these strategy contributions, vital architectural
-improvements to the library itself have also been received. You can see an
-overview of the structure of the source code in Figure~\ref{fig:overview}.
+To date the library has had contributions from 24 contributors from a variety of
+backgrounds. These contributions have been in terms of strategies. One strategy
+is the creation of an undergraduate mathematics student with little prior
+knowledge of programming. Multiple other strategies were written by a 15 year old
+secondary school student. As well as these strategy contributions, vital
+architectural improvements to the library itself have also been received. You
+can see an overview of the structure of the source code in
+Figure~\ref{fig:overview}.
 
@@
 		\centering
-		\includegraphics[width=.75\textwidth]{outline_of_library.pdf}
+		\includegraphics[width=\textwidth]{../img/outline_of_library.pdf}
 		\caption{An overview of the source code.}
@@
 		\centering
-		\includegraphics[width=.9\textwidth]{number_of_strategies_with_arima_projection.pdf}
+		\includegraphics[width=\textwidth]{../img/number_of_strategies_with_arima_projection.pdf}
 		\caption{The number of strategies included in the library}
@@
 
-\section*{New strategies, tournaments and implications}\label{sec:new-strategies-and-implications}
+Section~\ref{sec:new-strategies-and-implications} will describe in more detail
+some of research capabilities of the library.
+
+\section{New strategies, tournaments and implications}\label{sec:new-strategies-and-implications}
 
@@
 
-\begin{multicols}{2}
-    \begin{enumerate}[noitemsep,topsep=0pt]
+\begin{enumerate}
     \item Cooperator
@@
 \end{enumerate}
-\end{multicols}
 
@@
 	\centering
-	\includegraphics[width=.75\textwidth]{tournament.pdf}
+	\includegraphics[width=.9\textwidth]{../img/tournament.pdf}
 	\caption{Results from the library tournament (2016-03-31)}
@@
 
-\begin{itemize}[noitemsep,topsep=0pt]
+\begin{itemize}
     \item A closer look at zero determinant strategies, showing that
@@
 
-\section*{(2) Availability}\label{sec:availability}
-
-\section*{Operating system}
-
-The Axelrod library runs on all major operating systems: Linux, Mac OSX and
-Windows.
-
-\section*{Programming language}
-
-The library is continuously tested for Python 2.7, 3.3, 3.4 and 3.5.
-
-\section*{Additional system requirements}
-
-There are no specific additional system requirements.
-
-\section*{Support}
-
-Support is readily available in multiple forms:
-
-\begin{itemize}[noitemsep,topsep=0pt]
-    \item An online chat channel:
-        \url{https://gitter.im/Axelrod-Python/Axelrod}.
-    \item An  email group:
-        \url{https://groups.google.com/forum/#!topic/axelrod-python}.
-\end{itemize}
-
-\section*{Dependencies}
-
-The following Python libraries are required dependencies:
-
-\begin{multicols}{3}
-    \begin{itemize}[noitemsep,topsep=0pt]
-        \item Numpy 1.9.2:
-        \item Matplotlib 1.4.2:
-        \item Cloudpickle  0.1.1:
-        \item Hypothesis  3.0:
-        \item Testfixtures  4.9.1:
-    \end{itemize}
-\end{multicols}
-
-\section*{List of contributors}
-
-The names of all the contributors are not known: as these were mainly done
-through Github and certain have not provided their name or responded to a
-request for further details. Here is an incomplete list:
-
-\begin{multicols}{2}
-    \begin{itemize}[noitemsep,topsep=0pt]
-        \item {Owen Campbell}
-        \item {Mark Harper}
-        \item {Vincent Knight}
-        \item {Karol Langner}
-        \item {James Campbell}
-        \item {Thomas Campbell}
-        \item {Alex Carney}
-        \item {Martin Chorley}
-        \item {Cameron Davidson-Pilon}
-        \item {Kristian Glass}
-        \item {Tom{\'a}{\v s} Ehrlich}
-        \item {Martin Jones}
-        \item {Georgios Koutsovoulos}
-        \item {Marissa Tibble}
-        \item {Jochen M{\"u}ller}
-        \item {Geraint Palmer}
-        \item {Paul Slavin}
-        \item {Timothy Standen}
-        \item {Luis Visintini}
-        \item {Karl Molden}
-        \item {Jason Young}
-        \item {Andy Boot}
-        \item {Anna Barriscale}
-    \end{itemize}
-\end{multicols}
-
-\section*{Software location:}
-
-{\bf Archive}
-
-\begin{description}[noitemsep,topsep=0pt]
-    \item[Name:] Zenodo
-    \item[Persistent identifier:]
-\href{https://zenodo.org/record/45187}{10.5281/zenodo.45187}
-    \item[Licence:] MIT
-    \item[Publisher:]  Vincent Knight
-    \item[Version published:] Axelrod: Alternator Release. v0.0.28
-    \item[Date published:] 2016-01-26
-\end{description}
-
-{\bf Code repository}
-
-\begin{description}[noitemsep,topsep=0pt]
-    \item[Name:] Github
-    \item[Identifier:] \url{https://github.com/Axelrod-Python/Axelrod}
-    \item[Licence:] MIT
-    \item[Date published:] 2015-02-16
-\end{description}
-
-\section*{Reuse potential}\label{sec:reuse}
-
-The Axelrod library has been designed with sustainable software practice in
-mind. There is an extensive documentation suite:
-\url{axelrod.readthedocs.org/en/latest/}. Furthermore, there is a growing set
-of example Jupyter notebooks available here:
-\url{https://github.com/Axelrod-Python/Axelrod-notebooks}.
-
-The ability to have readily available a large number of strategies makes this
-tool an excellent and obvious example of the benefits of open research which
-should positively impact the game theoretic community.
-This has been evidenced by the work described: the library has already shown
-it's potential for reuse.
-
-\section*{Conclusion}
+\section{Conclusion}\label{sec:conclusion}
 
@@
 
-\begin{itemize}[noitemsep,topsep=0pt]
+\begin{itemize}
     \item Noisy tournaments;
@@
 
-\section*{Acknowledgements}
-
-The authors would like to thank all contributors. Also, they thank
-Robert Axelrod himself for his well wishes with the library.
-
-\section*{Competing interests}
-
-The authors declare that they have no competing interests.
+The ability to have readily available a large number of strategies makes this
+tool an excellent and obvious example of the benefits of open research which
+should positively impact the game theoretic community.
 

### 2016-06-02 tex/paper.tex
Correcting KML's affiliation.
Correcting Marc's name.
Correcting KMLs name in contrib list.
New title.
Resizing smaller images.

--- 2016-04-06 tex/paper.tex
@@
 
-An open reproducible framework for the study of the iterated prisoner's
+An open framework for the reproducible study of the iterated prisoner's
 dilemma.
@@
         \item Harper, Marc
-        \item Langner, Karol
+        \item Langner, Karol M.
         % All devs (alphabetic order of last name)
@@
 \item Development; Not affiliated
-\item Development; Not affiliated
+\item Development; Google Inc., Mountain View, CA
 \item Development; Cardiff University
@@
 \begin{figure}[!hbtp]
-    \begin{subfigure}{.5\textwidth}
 	\centering
@@
 	\label{fig:demo_tournament}
-    \end{subfigure}
-    \begin{subfigure}{.5\textwidth}
-        \centering
-        \includegraphics[width=.75\textwidth]{stewart_tournament.pdf}
-        \caption{The results from \cite{Stewart2012}.}
-        \label{fig:stewart_tournament}
-    \end{subfigure}
-    \caption{Summary plots produced by the library.}
 \end{figure}
@@
 \begin{figure}[!hbtp]
-    \begin{subfigure}{.5\textwidth}
 	\centering
-        \includegraphics[width=.75\textwidth]{outline_of_library.pdf}
+	\includegraphics[width=.9\textwidth]{outline_of_library.pdf}
 	\caption{An overview of the source code.}
 	\label{fig:overview}
-    \end{subfigure}
-    \begin{subfigure}{.5\textwidth}
-        \centering
-        \includegraphics[width=.9\textwidth]{number_of_strategies_with_arima_projection.pdf}
-        \caption{The number of strategies included in the library}
-        \label{fig:number_of_strategies_against_date}
-    \end{subfigure}
-    \caption{An overview of the library.}
 \end{figure}
@@
 grown at a fast pace, as can be seen in
-Figure~\ref{fig:number_of_strategies_against_date}. Despite this, due to
-previous research being done in an irreproducible manner with, for example, no
-source code and/or vaguely described strategies, not all previous tournaments
-can yet be reproduced. In fact, some of the early tournaments might be
-impossible to reproduce as the source code is forever lost. This library aims
-to prevent this from happening again in the future.
+Figure~\ref{fig:number_of_strategies_against_date}.
+
+\begin{figure}[!hbtp]
+	\centering
+	\includegraphics[width=.75\textwidth]{number_of_strategies_with_arima_projection.pdf}
+	\caption{The number of strategies included in the library}
+	\label{fig:number_of_strategies_against_date}
+\end{figure}
+
+Despite this, due to previous research being done in an irreproducible manner
+with, for example, no source code and/or vaguely described strategies, not all
+previous tournaments can yet be reproduced. In fact, some of the early
+tournaments might be impossible to reproduce as the source code is forever
+lost. This library aims to prevent this from happening again in the future.
 
@@
 the plot of Figure~\ref{fig:stewart_tournament}.
+
+\begin{figure}[!hbtp]
+	\centering
+	\includegraphics[width=.75\textwidth]{stewart_tournament.pdf}
+	\caption{The results from \cite{Stewart2012}.}
+	\label{fig:stewart_tournament}
+\end{figure}
 
@@
         \item {Owen Campbell}
-        \item {Mark Harper}
+        \item {Marc Harper}
         \item {Vincent Knight}
-        \item {Karol Langner}
+        \item {Karol M. Langner}
         \item {James Campbell}

### 2016-06-02 tex/paper.tex
Fixing some code snippets.
Also adding explanation about how to obtain full tournament results.

@@
 >>> plot = axelrod.Plot(results)
->>> plot.boxplot()
+>>> p = plot.boxplot()
+>>> p.show()
     \end{verbatim}
@@
 shows the results from the full tournament which can also be seen (in full
-detail) here: \url{http://axelrod-tournament.readthedocs.org/}.
+detail) here: \url{http://axelrod-tournament.readthedocs.org/}. Note that to
+obtain this tournament requires a simple change of the code shown in
+Figure~\ref{fig:demo_tournament_commands}, changing:
+
+\begin{verbatim}
+>>> strategies = [s() for s in axelrod.demo_strategies]}
+\end{verbatim}
+
+to:
+
+\begin{verbatim}
+>>> strategies = [s() for s in axelrod.ordinary_strategies]}.
+\end{verbatim}
 

### 2016-06-02 tex/paper.tex
Most smaller comments now addressed.
Still need work on library structure and/or reuse section.

@@
 Several Iterated Prisoner's Dilemma tournaments have generated much interest;
-including Axelrod's original tournaments \cite{Axelrod1980a,Axelrod1980b},
-two 2004 anniversary tournaments \cite{kendall2007iterated}, and
-the Stewart and Plotkin 2012 tournament \cite{Stewart2012}, following the
-discovery of zero-determinant strategies.  Subsequent research has spawned an
-enormous number of papers, but rarely are the results reproducible. Among
-well-known tournaments, in only one case is the full original source code
+Axelrod's original tournaments \cite{Axelrod1980a,Axelrod1980b}, two 2004
+anniversary tournaments \cite{kendall2007iterated}, and the Stewart and Plotkin
+2012 tournament \cite{Stewart2012}, following the discovery of zero-determinant
+strategies.  Subsequent research has spawned a number of papers (many of which
+are referenced throughout this paper), but rarely are the results reproducible.
+Amongst well-known tournaments, in only one case is the full original source code
 available (Axelrod's second tournament \cite{Axelrod1980b}, in FORTRAN). In no
-cases is the available code well-documented, easily modifiable, or released with
-significant test suites.
+cases is the available code well-documented, easily modifiable, or released
+with significant test suites.
 
@@
 
-This paper introduces a software package: the Axelrod Python library
+This paper introduces a software package: the Axelrod-Python library
 \cite{Axelrod-Pythonprojectteam2015}. The Axelrod-Python project has the
@@
         integrated tests with 99.37\% coverage (including property based tests:
-        \cite{Hypothesis3.0.3}
+        \cite{Hypothesis3.0.3})
     \item Well-documented: all features of the library are documented for ease of
@@
 The game of~(\ref{equ:one-shot}) is called the Prisoner's Dilemma. Specific
-numerical values of \((R,S,T,P)=(3,0,5,1)\) are often used in the literature,
-although any satisfying the conditions in~\ref{equ:one-shot} will yield similar
-results.  Axelrod's tournaments (and further implementations of these) are
-sometimes referred to as Iterated Prisoner's Dilemma (IPD) tournaments. An
-incomplete overview of published tournaments is given in
-Table~\ref{tab:tournaments}.
+numerical values of \((R,S,T,P)=(3,0,5,1)\) are often used in the literature
+\cite{Axelrod1980a, Axelrod1980b}, although any satisfying the conditions
+in~\ref{equ:one-shot} will yield similar results. Axelrod's tournaments (and
+further implementations of these) are sometimes referred to as Iterated
+Prisoner's Dilemma (IPD) tournaments. An incomplete representative overview of
+published tournaments is given in Table~\ref{tab:tournaments}.
 
@@
             1991     & \cite{Bendor1991}          & 13                   & Noisy    & Not immediately available\\
-            2002     & \cite{Stephens2002}        & 16                   & Wildlife & Not applicable\\
+            2002     & \cite{Stephens2002}        & 16                   & Wildlife & Not a computer based tournament\\
             2005     & \cite{kendall2007iterated} & 223                  & Varied   & Not available \\
@@
 standard Python installation package: `pip'
-(\url{https://pypi.python.org/pypi}). This ensures it can be used on all major
-operating systems (Windows, OS X and Linux).
+(\url{https://pypi.python.org/pypi}). The package name is \texttt{axelrod} and
+can thus be installed by calling: \texttt{pip install axelrod}. This ensures it
+can be used on all major operating systems (Windows, OS X and Linux).
 
@@
 \end{figure}
-
-Figure~\ref{fig:demo_tournament_commands} shows the very basic utilisation
-of the library and further details can be found at the online documentation:
-\url{http://axelrod.readthedocs.org}.
 
@@
 To date the library has had contributions from 24 contributors from a variety
-of backgrounds. These contributions have been in terms of strategies. One
-strategy is the creation of an undergraduate mathematics student with little
-prior knowledge of programming. Multiple other strategies were written by a 15
-year old secondary school student. Both of these students are authors of this
-paper. As well as these strategy contributions, vital architectural
-improvements to the library itself have also been received. You can see an
-overview of the structure of the source code in Figure~\ref{fig:overview}.
+of backgrounds which are not solely academic. These contributions have been in
+terms of strategies. One strategy is the creation of an undergraduate
+mathematics student with little prior knowledge of programming. Multiple other
+strategies were written by a 15 year old secondary school student. Both of
+these students are authors of this paper. As well as these strategy
+contributions, vital architectural improvements to the library itself have also
+been received.
+
+You can see an overview of the structure of the source code in
+Figure~\ref{fig:overview}. Add:
+
+\begin{itemize}
+	\item Discuss match generators (possibly include in image?)
+	\item Discuss what a strategy is (class, inheritance).
+	\item Reuse (possibility of creating new tournament types).
+\end{itemize}
 
@@
 This can be reproduced as shown in Figure~\ref{fig:stewart-code}, which gives
-the plot of Figure~\ref{fig:stewart_tournament}.
+the plot of Figure~\ref{fig:stewart_tournament}. Note that slight differences
+with the results of \cite{Stewart2012} are due to stochastic behaviour.
 
@@
 
-The current winning strategy is a novel strategy called: Looker Up. This is a
+The current winning strategy is a novel strategy: Looker Up. This is a
 strategy that maps a given set of states to actions. The state space is defined
@@
 of the framework for \(m=n=2\) for which a particle swarm algorithm has been
-used to train it, the second placed strategy was trained with an evolutionary
-algorithms. More details of this can be found in \cite{Jones2015, George2016}.
+used to train it. The second placed strategy was trained with an evolutionary
+algorithm \cite{Jones2015, George2016}.
 In \cite{Knight2015} experiments are described that evaluate how the second
@@
 There are various other insights that have been gained from ongoing open
-research on the library. These include:
+research on the library, details can be found in \cite{Harper2015}. These include:
 
@@
     \item A closer look at zero determinant strategies, showing that
-        extortionate strategies obtain a large number of wins \textit{but} do
-        not perform particularly well. This is relevant given the findings of
-        \cite{Stewart2012} in which zero determinant strategies are shown to be
-        able to perform better than any other strategy. This finding extends
-        to noisy tournaments (which are also implemented in the library).
+		extortionate strategies obtain a large number of wins: the number of
+		times they outscore an opponent during a given match. \textit{However} these do
+		not perform particularly well from the overall tournament ranking point of
+		view. This is relevant given the findings of \cite{Stewart2012} in which zero
+		determinant strategies are shown to be able to perform better than any other
+		strategy. This finding extends to noisy tournaments (which are also implemented
+		in the library).
     \item This negative relationship between wins and performance does not
@@
     \item Strategies like Looker Up and Meta Hunter seem to be generally
-        cooperative yet still exploit naive strategies. The MetaHunter strategy
+        cooperative yet still exploit naive strategies. The Meta Hunter strategy
         is a particular type of Meta strategy which uses a variety of other
@@
 
-Details for the above can be found in \cite{Harper2015}.
-
 \section*{(2) Availability}\label{sec:availability}
@@
 
-The Axelrod library runs on all major operating systems: Linux, Mac OSX and
+The Axelrod library runs on all major operating systems: Linux, Mac OS X and
 Windows.
@@
 
-The library is continuously tested for Python 2.7, 3.3, 3.4 and 3.5.
+The library is continuously tested for compatibility with Python 2.7, 3.4 and 3.5.
 
@@
         \item Matplotlib 1.4.2:
-        \item Cloudpickle  0.1.1:
         \item Hypothesis  3.0:
@@
 The names of all the contributors are not known: as these were mainly done
-through Github and certain have not provided their name or responded to a
+through Github and some have not provided their name or responded to a
 request for further details. Here is an incomplete list:
@@
 This has been evidenced by the work described: the library has already shown
-it's potential for reuse.
+its potential for reuse.
+
+Add more here: point to previous discussion about new strategies, new
+tournaments, tests etc\dots
 

### 2016-06-02 tex/response.tex
Early notes in response.

\documentclass{jors}

%% Set the header information

% Commenting out as this overrides the section titles.
\pagestyle{fancy}
\definecolor{mygray}{gray}{0.6}
\renewcommand\headrule{}
\rhead{\footnotesize 3}
\rhead{\textcolor{gray}{UP JORS software Latex paper template version 0.1}}

% Nicer bibliography management
\usepackage[backend=bibtex, firstinits=true, url=true, isbn=true]{biblatex}
\addbibresource{references.bib}
%-----------------------------

\usepackage{amsmath}  % Basic
\usepackage{booktabs}  % Better tables
\usepackage{graphicx}  % Images
\usepackage{hyperref}  % Links etc
% \usepackage{minted}  % Code: minted does not compile on arXiv
\usepackage{multicol}  % Multi column list
\usepackage{subcaption}  % Subfigures

\begin{document}
%% Set the header information
\pagestyle{fancy}
\definecolor{mygray}{gray}{0.6}
\renewcommand\headrule{}
\rhead{\footnotesize 3}
\rhead{\textcolor{gray}{UP JORS software Latex paper template version 0.1}}

\rule{\textwidth}{1pt}

\section*{(1) Overview}\label{sec:sec:overview}

\vspace{0.5cm}

\section*{Title}

Response to first review: An open framework for the reproducible study of the
iterated prisoner's dilemma.

\section*{Major comments}

\begin{itemize}
\item \textit{suggested title change}: This has been changed to ``An open framework for
      the reproducible study of the iterated prisoner's dilemma''
\item Implementation & Architecture section currently discusses how to use library, but should be refactored to expand upon architecture
\item \textit{Side-by-side figures appear too small, and should be replaced with full-size (perhaps top-bottom) figures}: Figures have been resized.
\item Discrepancy between version of software in paper and on Zenodo
\item \textif{Dependencies not automatically installed or checked via pip}: This has been addressed. Here is a url to the code patch (github pull request) that fixed this: \url{https://github.com/Axelrod-Python/Axelrod/pull/542}.
\end{itemize}

\section*{Minor comments}

Documentation paragraph in the prob end tournament section has been fixed. It now reads:

\begin{quote}
	We can also view the length of the matches played by each player. The plot
	shows that the length of each match (for each player) is not the same. The
	median length is 4 which is the expected value with the probability of a match
	ending being 0.5.
\end{quote}

The code snippets that were not complete (final line for plotting) have been
fixed. Furthermore, an explanation of how to obtain the full tournament results
has also been included.

The comment about variety of backgrounds: we feel that the paragraph explains what is meant (

The discussion group has been made public. This was an oversight.

Hypothesis is a requirement for development: cloudpickle is no longer a
requirement following some substanstial rewriting of the internals of the
library (resulting in speed, memory and readability improvements).

\end{document}

### 2016-06-03 tex/paper.tex
Minor details: update.
- Number of strategies
- Coverage percentage

@@
 
-The presented library is partly motivated by an ongoing discussion in the academic community
-about reproducible research \cite{Crick2014a, Hong2015a, Prlic2012, Sandve2013},
-and is:
+The presented library is partly motivated by an ongoing discussion in the
+academic community about reproducible research \cite{Crick2014a, Hong2015a,
+Prlic2012, Sandve2013}, and is:
 
@@
     \item Reproducible and well-tested: at the time of writing there is an excellent level of
-        integrated tests with 99.37\% coverage (including property based tests:
+        integrated tests with 99.73\% coverage (including property based tests:
         \cite{Hypothesis3.0.3})
@@
         use and modification
-    \item Extensive: 123 strategies are included, with infinitely-many
-        strategies available in the case of parametrised strategies
+    \item Extensive: 135 strategies are included, with infinitely-many
+        available in the case of parametrised strategies
     \item Extensible: easy to modify to include new strategies and to run new tournaments

### 2016-06-03 tex/paper.tex
Adding a paragraph about the structure of the library.
Also, moving some of the examples to reuse.
Not sure if this fully gets what the reviewer wanted.

@@
 strategies for this evolutionary study. This is noteworthy as
-\cite{Axelrod-Pythonprojectteam2015} now boasts over 120 strategies that are
+\cite{Axelrod-Pythonprojectteam2015} now boasts over 135 strategies that are
 readily available for a similar analysis.
@@
 
-Figure~\ref{fig:demo_tournament_commands} shows a very simple example of using
-the library to create a basic tournament giving the graphical output shown in
-Figure~\ref{fig:demo_tournament}.
-
-\begin{figure}[!hbtp]
-    \begin{verbatim}
->>> import axelrod
->>> strategies = [s() for s in axelrod.demo_strategies]
->>> tournament = axelrod.Tournament(strategies)
->>> results = tournament.play()
->>> plot = axelrod.Plot(results)
->>> p = plot.boxplot()
->>> p.show()
-    \end{verbatim}
-    \caption{A simple set of commands to create a demonstration tournament. The
-        output is shown in Figure~\ref{fig:demo_tournament}.}
-    \label{fig:demo_tournament_commands}
-\end{figure}
-
-\begin{figure}[!hbtp]
-	\centering
-	\includegraphics[width=.75\textwidth]{demo_tournament.pdf}
-	\caption{The results from a simple tournament.}
-	\label{fig:demo_tournament}
-\end{figure}
-
-As stated in the \textbf{Introduction}, one of the main goals of the library
-is to allow for the easy contribution of strategies. Doing this requires the
+As stated in the \textbf{Introduction}, one of the main goals of the library is
+to allow for the easy contribution of strategies. Doing this requires the
 writing of a simple Python class (which can inherit from other predefined
-classes). Full contribution guidelines can be found in the documentation.
-As an example, Figures~\ref{fig:grudger} and~\ref{fig:grudger_test} show the source code for
-the Grudger strategy as well as its corresponding test.
+classes). All components of the library are automatically tested using a
+combination of unit, property and integration tests, these tests are run as new
+features are added to the library to ensure compatibility. Thus, when submitting
+a strategy, a simple test is required which ensures the strategy behaves as
+expected.
+Full contribution guidelines can be found in the documentation.  As an
+example, Figures~\ref{fig:grudger} and~\ref{fig:grudger_test} show the source
+code for the Grudger strategy as well as its corresponding test.
 
@@
 
-To date the library has had contributions from 24 contributors from a variety
+You can see an overview of the structure of the source code in
+Figure~\ref{fig:overview}. This shows the parallel collection of strategies and
+their tests. Furthermore the underlying engine for the library is a class for
+tournaments which lives in the \texttt{tournament.py} module. This class is
+responsible for coordinating the play of generated matches. This generation of
+matches is the responsibility of a match generator class which is designed in
+such a way as to be easily modifiable to create new types of matches. This is
+described fuller in a tutorial in the documentation which shows how to easily
+create a tournament where players only play each other with probability 0.5.
+This will be discussed further in the reuse section of this paper.
+
+\begin{figure}[!hbtp]
+	\centering
+	\includegraphics[width=.9\textwidth]{outline_of_library.pdf}
+	\caption{An overview of the source code.}
+	\label{fig:overview}
+\end{figure}
+
+To date the library has had contributions from 25 contributors from a variety
 of backgrounds which are not solely academic. These contributions have been in
@@
 been received.
-
-You can see an overview of the structure of the source code in
-Figure~\ref{fig:overview}. Add:
-
-\begin{itemize}
-	\item Discuss match generators (possibly include in image?)
-	\item Discuss what a strategy is (class, inheritance).
-	\item Reuse (possibility of creating new tournament types).
-\end{itemize}
-
-\begin{figure}[!hbtp]
-	\centering
-	\includegraphics[width=.9\textwidth]{outline_of_library.pdf}
-	\caption{An overview of the source code.}
-	\label{fig:overview}
-\end{figure}
 
@@
 
-\begin{multicols}{3}
+\begin{multicols}{2}
     \begin{itemize}[noitemsep,topsep=0pt]
-        \item Numpy 1.9.2:
-        \item Matplotlib 1.4.2:
-        \item Hypothesis  3.0:
-        \item Testfixtures  4.9.1:
+        \item Numpy 1.9.2
+        \item Matplotlib 1.4.2
+        \item Testfixtures 4.9.1
+        \item Hypothesis 3.0 (only a requirement for development)
     \end{itemize}
@@
 
+Figure~\ref{fig:demo_tournament_commands} shows a very simple example of using
+the library to create a basic tournament giving the graphical output shown in
+Figure~\ref{fig:demo_tournament}.
+
+\begin{figure}[!hbtp]
+    \begin{verbatim}
+>>> import axelrod
+>>> strategies = [s() for s in axelrod.demo_strategies]
+>>> tournament = axelrod.Tournament(strategies)
+>>> results = tournament.play()
+>>> plot = axelrod.Plot(results)
+>>> p = plot.boxplot()
+>>> p.show()
+    \end{verbatim}
+    \caption{A simple set of commands to create a demonstration tournament. The
+        output is shown in Figure~\ref{fig:demo_tournament}.}
+    \label{fig:demo_tournament_commands}
+\end{figure}
+
+\begin{figure}[!hbtp]
+	\centering
+	\includegraphics[width=.75\textwidth]{demo_tournament.pdf}
+	\caption{The results from a simple tournament.}
+	\label{fig:demo_tournament}
+\end{figure}
+
 The Axelrod library has been designed with sustainable software practice in

### 2016-06-03 tex/paper.tex
New plots.
- Removing the ARIMA for number of strategies
- Rerunning the plot for the full tournament
More restructuring.

@@
 
-With a growing collection of 122 strategies, the library is a also a
+With a growing collection of 135 strategies, the library is a also a
 platform for an original tournament that, in itself, is of interest to the
@@
         available in the case of parametrised strategies
-    \item Extensible: easy to modify to include new strategies and to run new tournaments
+    \item Extensible: easy to modify to include new strategies and to run new
+        tournaments
 \end{itemize}
@@
 
-Installation of the library is straightforward as it is available via the
-standard Python installation package: `pip'
-(\url{https://pypi.python.org/pypi}). The package name is \texttt{axelrod} and
-can thus be installed by calling: \texttt{pip install axelrod}. This ensures it
-can be used on all major operating systems (Windows, OS X and Linux).
-
 As stated in the \textbf{Introduction}, one of the main goals of the library is
@@
 tournaments which lives in the \texttt{tournament.py} module. This class is
-responsible for coordinating the play of generated matches. This generation of
-matches is the responsibility of a match generator class which is designed in
-such a way as to be easily modifiable to create new types of matches. This is
-described fuller in a tutorial in the documentation which shows how to easily
-create a tournament where players only play each other with probability 0.5.
-This will be discussed further in the reuse section of this paper.
+responsible for coordinating the play of generated matches (from the
+\texttt{match.py} module). This generation of matches is the responsibility of a
+match generator class (in the \texttt{match\_generator.py} module) which is
+designed in such a way as to be easily modifiable to create new types of
+tournaments. This is described fuller in a tutorial in the documentation which
+shows how to easily create a tournament where players only play each other with
+probability 0.5.  This will be discussed further in the reuse section of this
+paper.
 
@@
 been received.
+
+\section*{(2) Availability}\label{sec:availability}
+
+\section*{Operating system}
+
+The Axelrod library runs on all major operating systems: Linux, Mac OS X and
+Windows.
+
+\section*{Programming language}
+
+The library is continuously tested for compatibility with Python 2.7, 3.4 and 3.5.
+
+\section*{Additional system requirements}
+
+There are no specific additional system requirements.
+
+\section*{Support}
+
+Support is readily available in multiple forms:
+
+\begin{itemize}[noitemsep,topsep=0pt]
+    \item An online chat channel:
+        \url{https://gitter.im/Axelrod-Python/Axelrod}.
+    \item An  email group:
+        \url{https://groups.google.com/forum/#!topic/axelrod-python}.
+\end{itemize}
+
+\section*{Dependencies}
+
+The following Python libraries are required dependencies:
+
+\begin{multicols}{2}
+    \begin{itemize}[noitemsep,topsep=0pt]
+        \item Numpy 1.9.2
+        \item Matplotlib 1.4.2
+        \item Testfixtures 4.9.1
+        \item Hypothesis 3.0 (only a requirement for development)
+    \end{itemize}
+\end{multicols}
+
+\section*{List of contributors}
+
+The names of all the contributors are not known: as these were mainly done
+through Github and some have not provided their name or responded to a
+request for further details. Here is an incomplete list:
+
+\begin{multicols}{2}
+    \begin{itemize}[noitemsep,topsep=0pt]
+        \item {Owen Campbell}
+        \item {Marc Harper}
+        \item {Vincent Knight}
+        \item {Karol M. Langner}
+        \item {James Campbell}
+        \item {Thomas Campbell}
+        \item {Alex Carney}
+        \item {Martin Chorley}
+        \item {Cameron Davidson-Pilon}
+        \item {Kristian Glass}
+        \item {Tom{\'a}{\v s} Ehrlich}
+        \item {Martin Jones}
+        \item {Georgios Koutsovoulos}
+        \item {Marissa Tibble}
+        \item {Jochen M{\"u}ller}
+        \item {Geraint Palmer}
+        \item {Paul Slavin}
+        \item {Timothy Standen}
+        \item {Luis Visintini}
+        \item {Karl Molden}
+        \item {Jason Young}
+        \item {Andy Boot}
+        \item {Anna Barriscale}
+    \end{itemize}
+\end{multicols}
+
+\section*{Software location:}
+
+{\bf Archive}
+
+\begin{description}[noitemsep,topsep=0pt]
+    \item[Name:] Zenodo
+    \item[Persistent identifier:]
+\href{https://zenodo.org/record/45187}{10.5281/zenodo.45187}
+    \item[Licence:] MIT
+    \item[Publisher:]  Vincent Knight
+    \item[Version published:] Axelrod: Alternator Release. v0.0.28
+    \item[Date published:] 2016-01-26
+\end{description}
+
+{\bf Code repository}
+
+\begin{description}[noitemsep,topsep=0pt]
+    \item[Name:] Github
+    \item[Identifier:] \url{https://github.com/Axelrod-Python/Axelrod}
+    \item[Licence:] MIT
+    \item[Date published:] 2015-02-16
+\end{description}
+
+\section*{Reuse potential}\label{sec:reuse}
+
+The Axelrod library has been designed with sustainable software practice in
+mind. There is an extensive documentation suite:
+\url{axelrod.readthedocs.org/en/latest/}. Furthermore, there is a growing set
+of example Jupyter notebooks available here:
+\url{https://github.com/Axelrod-Python/Axelrod-notebooks}.
+
+The ability to have readily available a large number of strategies makes this
+tool an excellent and obvious example of the benefits of open research which
+should positively impact the game theoretic community.
+This has been evidenced by the work described: the library has already shown
+its potential for reuse.
+
+Installation of the library is straightforward as it is available via the
+standard Python installation package: `pip'
+(\url{https://pypi.python.org/pypi}). The package name is \texttt{axelrod} and
+can thus be installed by calling: \texttt{pip install axelrod}. This ensures it
+can be used on all major operating systems (Windows, OS X and Linux).
+
+Figure~\ref{fig:demo_tournament_commands} shows a very simple example of using
+the library to create a basic tournament giving the graphical output shown in
+Figure~\ref{fig:demo_tournament}.
+
+\begin{figure}[!hbtp]
+    \begin{verbatim}
+>>> import axelrod
+>>> strategies = [s() for s in axelrod.demo_strategies]
+>>> tournament = axelrod.Tournament(strategies)
+>>> results = tournament.play()
+>>> plot = axelrod.Plot(results)
+>>> p = plot.boxplot()
+>>> p.show()
+    \end{verbatim}
+    \caption{A simple set of commands to create a demonstration tournament. The
+        output is shown in Figure~\ref{fig:demo_tournament}.}
+    \label{fig:demo_tournament_commands}
+\end{figure}
+
+\begin{figure}[!hbtp]
+	\centering
+	\includegraphics[width=.75\textwidth]{demo_tournament.pdf}
+	\caption{The results from a simple tournament.}
+	\label{fig:demo_tournament}
+\end{figure}
 
@@
 
-\section*{(2) Availability}\label{sec:availability}
-
-\section*{Operating system}
-
-The Axelrod library runs on all major operating systems: Linux, Mac OS X and
-Windows.
-
-\section*{Programming language}
-
-The library is continuously tested for compatibility with Python 2.7, 3.4 and 3.5.
-
-\section*{Additional system requirements}
-
-There are no specific additional system requirements.
-
-\section*{Support}
-
-Support is readily available in multiple forms:
-
-\begin{itemize}[noitemsep,topsep=0pt]
-    \item An online chat channel:
-        \url{https://gitter.im/Axelrod-Python/Axelrod}.
-    \item An  email group:
-        \url{https://groups.google.com/forum/#!topic/axelrod-python}.
-\end{itemize}
-
-\section*{Dependencies}
-
-The following Python libraries are required dependencies:
-
-\begin{multicols}{2}
-    \begin{itemize}[noitemsep,topsep=0pt]
-        \item Numpy 1.9.2
-        \item Matplotlib 1.4.2
-        \item Testfixtures 4.9.1
-        \item Hypothesis 3.0 (only a requirement for development)
-    \end{itemize}
-\end{multicols}
-
-\section*{List of contributors}
-
-The names of all the contributors are not known: as these were mainly done
-through Github and some have not provided their name or responded to a
-request for further details. Here is an incomplete list:
-
-\begin{multicols}{2}
-    \begin{itemize}[noitemsep,topsep=0pt]
-        \item {Owen Campbell}
-        \item {Marc Harper}
-        \item {Vincent Knight}
-        \item {Karol M. Langner}
-        \item {James Campbell}
-        \item {Thomas Campbell}
-        \item {Alex Carney}
-        \item {Martin Chorley}
-        \item {Cameron Davidson-Pilon}
-        \item {Kristian Glass}
-        \item {Tom{\'a}{\v s} Ehrlich}
-        \item {Martin Jones}
-        \item {Georgios Koutsovoulos}
-        \item {Marissa Tibble}
-        \item {Jochen M{\"u}ller}
-        \item {Geraint Palmer}
-        \item {Paul Slavin}
-        \item {Timothy Standen}
-        \item {Luis Visintini}
-        \item {Karl Molden}
-        \item {Jason Young}
-        \item {Andy Boot}
-        \item {Anna Barriscale}
-    \end{itemize}
-\end{multicols}
-
-\section*{Software location:}
-
-{\bf Archive}
-
-\begin{description}[noitemsep,topsep=0pt]
-    \item[Name:] Zenodo
-    \item[Persistent identifier:]
-\href{https://zenodo.org/record/45187}{10.5281/zenodo.45187}
-    \item[Licence:] MIT
-    \item[Publisher:]  Vincent Knight
-    \item[Version published:] Axelrod: Alternator Release. v0.0.28
-    \item[Date published:] 2016-01-26
-\end{description}
-
-{\bf Code repository}
-
-\begin{description}[noitemsep,topsep=0pt]
-    \item[Name:] Github
-    \item[Identifier:] \url{https://github.com/Axelrod-Python/Axelrod}
-    \item[Licence:] MIT
-    \item[Date published:] 2015-02-16
-\end{description}
-
-\section*{Reuse potential}\label{sec:reuse}
-
-Figure~\ref{fig:demo_tournament_commands} shows a very simple example of using
-the library to create a basic tournament giving the graphical output shown in
-Figure~\ref{fig:demo_tournament}.
-
-\begin{figure}[!hbtp]
-    \begin{verbatim}
->>> import axelrod
->>> strategies = [s() for s in axelrod.demo_strategies]
->>> tournament = axelrod.Tournament(strategies)
->>> results = tournament.play()
->>> plot = axelrod.Plot(results)
->>> p = plot.boxplot()
->>> p.show()
-    \end{verbatim}
-    \caption{A simple set of commands to create a demonstration tournament. The
-        output is shown in Figure~\ref{fig:demo_tournament}.}
-    \label{fig:demo_tournament_commands}
-\end{figure}
-
-\begin{figure}[!hbtp]
-	\centering
-	\includegraphics[width=.75\textwidth]{demo_tournament.pdf}
-	\caption{The results from a simple tournament.}
-	\label{fig:demo_tournament}
-\end{figure}
-
-The Axelrod library has been designed with sustainable software practice in
-mind. There is an extensive documentation suite:
-\url{axelrod.readthedocs.org/en/latest/}. Furthermore, there is a growing set
-of example Jupyter notebooks available here:
-\url{https://github.com/Axelrod-Python/Axelrod-notebooks}.
-
-The ability to have readily available a large number of strategies makes this
-tool an excellent and obvious example of the benefits of open research which
-should positively impact the game theoretic community.
-This has been evidenced by the work described: the library has already shown
-its potential for reuse.
-
-Add more here: point to previous discussion about new strategies, new
-tournaments, tests etc\dots
-
 \section*{Conclusion}

### 2016-06-03 tex/paper.tex
Adding Moran processes to what the library can do.
Removing self references.

@@
 
-This paper introduces a software package: the Axelrod-Python library
-\cite{Axelrod-Pythonprojectteam2015}. The Axelrod-Python project has the
-following stated goals:
+This paper introduces a software package: the Axelrod-Python library. The
+Axelrod-Python project has the following stated goals:
 
@@
 strategies for this evolutionary study. This is noteworthy as
-\cite{Axelrod-Pythonprojectteam2015} now boasts over 135 strategies that are
+the library now boasts over 135 strategies that are
 readily available for a similar analysis.
@@
 	\centering
-	\includegraphics[width=.75\textwidth]{number_of_strategies_with_arima_projection.pdf}
+	\includegraphics[width=.75\textwidth]{number_of_strategies.pdf}
 	\caption{The number of strategies included in the library}
@@
     \item Ecological analysis of tournaments.
+    \item Moran processes.
     \item Morality metrics based on \cite{Singer-Clark2014}.

### 2016-06-03 tex/paper.tex
Fixing various details.
- Moran processes
- Data is available
- Mention readthedocs and travis.ci

@@
 combination of unit, property and integration tests, these tests are run as new
-features are added to the library to ensure compatibility. Thus, when submitting
-a strategy, a simple test is required which ensures the strategy behaves as
-expected.
-Full contribution guidelines can be found in the documentation.  As an
-example, Figures~\ref{fig:grudger} and~\ref{fig:grudger_test} show the source
-code for the Grudger strategy as well as its corresponding test.
+features are added to the library to ensure compatibility (they are also run
+automatically using \url{travis-ci.org}). Thus, when submitting a strategy, a
+simple test is required which ensures the strategy behaves as expected.  Full
+contribution guidelines can be found in the documentation, which is also part of
+the library itself and is hosted using \url{readthedocs.org}.  As an example,
+Figures~\ref{fig:grudger} and~\ref{fig:grudger_test} show the source code for
+the Grudger strategy as well as its corresponding test.
 
@@
     \item[Persistent identifier:]
-\href{https://zenodo.org/record/45187}{10.5281/zenodo.45187}
+\href{https://zenodo.org/record/53982}{10.5281/zenodo.53982}
     \item[Licence:] MIT
     \item[Publisher:]  Vincent Knight
-    \item[Version published:] Axelrod: Alternator Release. v0.0.28
-    \item[Date published:] 2016-01-26
+    \item[Version published:] Axelrod: 1.1.1
+    \item[Date published:] 2016-06-01
 \end{description}
@@
 shows the results from the full tournament which can also be seen (in full
-detail) here: \url{http://axelrod-tournament.readthedocs.org/}. Note that to
+detail) here: \url{http://axelrod-tournament.readthedocs.org/}. Data sets are
+also available showing the plays of every match that takes place. Note that to
 obtain this tournament requires a simple change of the code shown in
@@
     \includegraphics[width=.75\textwidth]{tournament.pdf}
-    \caption{Results from the library tournament (2016-03-31)}
+    \caption{Results from the library tournament (2016-06-01)}
     \label{fig:tournament}

### 2016-06-03 tex/response.tex
Tidying response.

@@
-\documentclass{jors}
+\documentclass{article}
 
-%% Set the header information
+\usepackage{fullpage}
+\usepackage{parskip}
+\usepackage{hyperref}
 
-% Commenting out as this overrides the section titles.
-\pagestyle{fancy}
-\definecolor{mygray}{gray}{0.6}
-\renewcommand\headrule{}
-\rhead{\footnotesize 3}
-\rhead{\textcolor{gray}{UP JORS software Latex paper template version 0.1}}
-
-% Nicer bibliography management
-\usepackage[backend=bibtex, firstinits=true, url=true, isbn=true]{biblatex}
-\addbibresource{references.bib}
-%-----------------------------
-
-\usepackage{amsmath}  % Basic
-\usepackage{booktabs}  % Better tables
-\usepackage{graphicx}  % Images
-\usepackage{hyperref}  % Links etc
-% \usepackage{minted}  % Code: minted does not compile on arXiv
-\usepackage{multicol}  % Multi column list
-\usepackage{subcaption}  % Subfigures
+\title{Response to review: An open framework for the reproducible study of the
+iterated prisoner's dilemma.}
+\date{\today}
 
 \begin{document}
-%% Set the header information
-\pagestyle{fancy}
-\definecolor{mygray}{gray}{0.6}
-\renewcommand\headrule{}
-\rhead{\footnotesize 3}
-\rhead{\textcolor{gray}{UP JORS software Latex paper template version 0.1}}
 
-\rule{\textwidth}{1pt}
+\maketitle
 
-\section*{(1) Overview}\label{sec:sec:overview}
+We would like to note that the reviewers provided a thorough and high quality
+review of our paper. We are grateful for this and thankful for all of their
+suggestions as we feel it greatly strengthens our manuscript.
 
-\vspace{0.5cm}
-
-\section*{Title}
-
-Response to first review: An open framework for the reproducible study of the
-iterated prisoner's dilemma.
-
-\section*{Major comments}
+\section{Major comments}
 
 \begin{itemize}
-\item \textit{suggested title change}: This has been changed to ``An open framework for
-      the reproducible study of the iterated prisoner's dilemma''
-\item Implementation & Architecture section currently discusses how to use library, but should be refactored to expand upon architecture
-\item \textit{Side-by-side figures appear too small, and should be replaced with full-size (perhaps top-bottom) figures}: Figures have been resized.
-\item Discrepancy between version of software in paper and on Zenodo
-\item \textif{Dependencies not automatically installed or checked via pip}: This has been addressed.
-Here is a url to the code patch (github pull request) that fixed this: \url{https://github.com/Axelrod-Python/Axelrod/pull/542}.
+\item \textit{suggested title change}: This has been changed to ``An open
+    framework for the reproducible study of the iterated prisoner's dilemma''
+\item \textit{Implementation \& Architecture section currently discusses how to
+    use library, but should be refactored to expand upon architecture}: The
+    various examples have been moved to the Reuse section and an extra paragraph
+    explaining the structure has been added.
+\item \textit{Side-by-side figures appear too small, and should be replaced with
+    full-size (perhaps top-bottom) figures}: Figures have been resized.
+\item \textit{Discrepancy between version of software in paper and on Zenodo}:
+    This has been addressed.
+\item \textit{Dependencies not automatically installed or checked via pip}: This
+    has been addressed. Here is a url to the code patch (github pull request)
+    that fixed this: \url{https://github.com/Axelrod-Python/Axelrod/pull/542}.
 \end{itemize}
 
-\section*{Minor comments}
+\section{Minor comments}
 
-Documentation paragraph in the prob end tournament section has been fixed. It now reads:
+We have addressed almost all of the minor comments: these can be viewed in
+detail here: \url{PR goes here}.
+
+Some of these we comment here for ease of review:
+
+Documentation paragraph in the prob end tournament section has been fixed. It
+now reads:
 
@@
     shows that the length of each match (for each player) is not the same. The
-	median length is 4 which is the expected value with the probability of a match
-	ending being 0.5.
+    median length is 4 which is the expected value with the probability of a
+    match ending being 0.5.
 \end{quote}
@@
 
-The comment about variety of backgrounds: we feel that the paragraph explains what is meant (
-
 The discussion group has been made public. This was an oversight.
 
+Regarding the urls that were not correct in the bibliography: we have removed
+these for the present time and will leave the formatting/requirements for these
+till the editorial process. Note that the ones we have removed correspond to
+well referenced published pieces of work and so removing the urls does not
+hinder finding the sources.
+
+One comment we have not addressed is with regards to hypothesis not being a
+requirement.
 Hypothesis is a requirement for development: cloudpickle is no longer a
-requirement following some substanstial rewriting of the internals of the
+requirement following some substantial rewriting of the internals of the
 library (resulting in speed, memory and readability improvements).

### 2016-06-03 tex/paper.tex
Removing a blank space.
Tidying response.

@@
 % Nicer bibliography management
-\usepackage[backend=bibtex, firstinits=true, url=true, isbn=true]{biblatex}
+\usepackage[backend=bibtex, firstinits=true, url=false, isbn=true]{biblatex}
 \addbibresource{references.bib}
@@
 >>> import axelrod
-
 >>> strategies = [axelrod.Cooperator(),
@@
     \item Parallelization of computations for tournaments with a high
-        computational cost \cite{Pathos, Mckerns2011}.
+        computational cost.
 \end{itemize}

### 2016-06-03 tex/response.tex
Adding the diff.

@@
 
-We have addressed almost all of the minor comments: these can be viewed in
-detail here: \url{PR goes here}.
+We have addressed almost all of the minor comments, these can be viewed in
+detail here:
+\url{https://github.com/Axelrod-Python/An-open-reproducible-framework-for-the-study-of-the-iterated-prisoners-dilemma/compare/jors...jors-r1-vk}.
 

### 2016-06-07 tex/paper.tex
Comments from Marc.

@@
 classes). All components of the library are automatically tested using a
-combination of unit, property and integration tests, these tests are run as new
+combination of unit, property and integration tests. These tests are run as new
 features are added to the library to ensure compatibility (they are also run
-automatically using \url{travis-ci.org}). Thus, when submitting a strategy, a
+automatically using \url{travis-ci.org}). When submitting a strategy, a
 simple test is required which ensures the strategy behaves as expected.  Full
@@
 \texttt{match.py} module). This generation of matches is the responsibility of a
-match generator class (in the \texttt{match\_generator.py} module) which is
-designed in such a way as to be easily modifiable to create new types of
-tournaments. This is described fuller in a tutorial in the documentation which
-shows how to easily create a tournament where players only play each other with
-probability 0.5.  This will be discussed further in the reuse section of this
-paper.
+\textit{match generator} class (in the \texttt{match\_generator.py} module)
+which is designed in such a way as to be easily modifiable to create new types
+of tournaments. This is described further in a tutorial in the documentation
+which shows how to easily create a tournament where players only play each other
+with probability 0.5.  This will be discussed further in the reuse section of
+this paper.
 
@@
 
-To date the library has had contributions from 25 contributors from a variety
-of backgrounds which are not solely academic. These contributions have been in
-terms of strategies. One strategy is the creation of an undergraduate
+To date the library has had contributions from 25 contributors from a variety of
+backgrounds which are not solely academic. These contributions have been mostly
+in terms of strategies. One strategy is the creation of an undergraduate
 mathematics student with little prior knowledge of programming. Multiple other
-strategies were written by a 15 year old secondary school student. Both of
-these students are authors of this paper. As well as these strategy
-contributions, vital architectural improvements to the library itself have also
-been received.
+strategies were written by a 15 year old secondary school student. Both of these
+students are authors of this paper. As well as these strategy contributions,
+vital architectural improvements to the library itself have also been
+contributed.
 
@@
 
-The library is continuously tested for compatibility with Python 2.7, 3.4 and 3.5.
+The library is continuously tested for compatibility with Python 2.7 and the two
+most recent python 3 releases.
 
@@
         \item Numpy 1.9.2
-        \item Matplotlib 1.4.2
-        \item Testfixtures 4.9.1
+        \item Matplotlib 1.4.2 (only a requirement if graphical output is
+            required)
+        \item Tqdm 3.4.0
         \item Hypothesis 3.0 (only a requirement for development)
@@
 
-The Axelrod library has been designed with sustainable software practice in
+The Axelrod library has been designed with sustainable software practices in
 mind. There is an extensive documentation suite:
@@
 
-The ability to have readily available a large number of strategies makes this
+The availability of a large number of strategies makes this
 tool an excellent and obvious example of the benefits of open research which
-should positively impact the game theoretic community.
-This has been evidenced by the work described: the library has already shown
-its potential for reuse.
+should positively impact the game theory community.
+This is evidently true already as the library has been used to study and create
+interesting and powerful new strategies.
 
-Installation of the library is straightforward as it is available via the
-standard Python installation package: `pip'
-(\url{https://pypi.python.org/pypi}). The package name is \texttt{axelrod} and
-can thus be installed by calling: \texttt{pip install axelrod}. This ensures it
-can be used on all major operating systems (Windows, OS X and Linux).
+Installation of the library is straightforward via standard python installation
+repositories (\url{https://pypi.python.org/pypi}). The package name is
+\texttt{axelrod} and can thus be installed by calling: \texttt{pip install
+axelrod} on all major operating systems (Windows, OS X and Linux).
 
@@
 
-Despite this, due to previous research being done in an irreproducible manner
+Nevertheless, due to previous research being done in an irreproducible manner
 with, for example, no source code and/or vaguely described strategies, not all
 previous tournaments can yet be reproduced. In fact, some of the early
-tournaments might be impossible to reproduce as the source code is forever
-lost. This library aims to prevent this from happening again in the future.
+tournaments might be impossible to reproduce as the source code is apparently
+forever lost. This library aims ensure reproducibility in the future.
 
@@
 the plot of Figure~\ref{fig:stewart_tournament}. Note that slight differences
-with the results of \cite{Stewart2012} are due to stochastic behaviour.
+with the results of \cite{Stewart2012} are due to stochastic behaviour of some
+strategies.
 
@@
 also available showing the plays of every match that takes place. Note that to
-obtain this tournament requires a simple change of the code shown in
-Figure~\ref{fig:demo_tournament_commands}, changing:
+recreate this tournament simply requires changing a single line of the code
+shown in Figure~\ref{fig:demo_tournament_commands}, changing:
 
@@
 
-The current winning strategy is a novel strategy: Looker Up. This is a
-strategy that maps a given set of states to actions. The state space is defined
-generically by \(m, n\) so as to map states to actions as shown
+The current winning strategy is new to the research literature: Looker Up. This
+is a strategy that maps a given set of states to actions. The state space is
+defined generically by \(m, n\) so as to map states to actions as shown
 in~(\ref{equ:example_of_lookerup}).

### 2016-06-10 tex/paper.tex
Changes suggested by Owen.

@@
         \item Glass, Kristian
+        \item Glynatsi, Nikoleta
         \item Ehrlich Tom{\'a}{\v s}
@@
 \item Development; Not affiliated
+\item Development; Cardiff University
 \item Development; Not affiliated
@@
 
-With a growing collection of 135 strategies, the library is a also a
+With a growing collection of 136 strategies, the library is a also a
 platform for an original tournament that, in itself, is of interest to the
@@
 
-To make matters more complicated, often a newly-created strategy is studied in
-isolation by opponents chosen by the strategy's creators, and often such
-strategies are not sufficiently described to enable reliable recreation
-(in the absence of source code), with \cite{slany2007some} being a notable
-counter-example. In some cases, strategies are revised without updates to their
-names or published implementations \cite{li2007design, li2011engineering}.
-As a result, some of the results related to these strategies and tournaments
-cannot be reliably replicated, and therefore have not met the basic scientific
-criterion of falsifiability.
+To complicate matters further, a new strategy is often studied in isolation
+with opponents chosen by the creator of that strategy. Often such strategies
+are not sufficiently described to enable reliable recreation (in the absence of
+source code), with \cite{slany2007some} being a notable counter-example. In
+some cases, strategies are revised without updates to their names or published
+implementations \cite{li2007design, li2011engineering}.
+As such, the results cannot be reliably replicated and therefore have not met
+the basic scientific criterion of falsifiability.
 
@@
 strategies for this evolutionary study. This is noteworthy as
-the library now boasts over 135 strategies that are
+the library now boasts over 136 strategies that are
 readily available for a similar analysis.
@@
 
-To date the library has had contributions from 25 contributors from a variety of
+To date the library has had contributions from 26 contributors from a variety of
 backgrounds which are not solely academic. These contributions have been mostly
@@
         \item {Kristian Glass}
+        \item {Nikoleta Glynatsi}
         \item {Tom{\'a}{\v s} Ehrlich}

### 2016-06-14 tex/response.tex

@@
 
+The copyright section of the license has been reworded. A discussion of this can
+be viewed here: \url{https://github.com/Axelrod-Python/Axelrod/issues/615}.
+
 The code snippets that were not complete (final line for plotting) have been
@@
 One comment we have not addressed is with regards to hypothesis not being a
-requirement.
-Hypothesis is a requirement for development: cloudpickle is no longer a
-requirement following some substantial rewriting of the internals of the
-library (resulting in speed, memory and readability improvements).
+requirement.  Hypothesis is a requirement for development. Cloudpickle is no
+longer a requirement following some substantial rewriting of the internals of
+the library (resulting in speed, memory and readability improvements).
+TestFixtures is also, no longer a requirement.
+
+Other changes include updating the figures showing the number of strategies and
+the latest run of the tournament as well as including another author: due to the
+fact that they contributed a new strategy while the paper was under review.
+
+Furthermore, we have made some minor changes to the text. These were all minor
+typographical changes aimed at improving the readability of the manuscript.
 
